---
title: "Descriptive Analysis of ASU Survey for Quarterly Report 1/1 through 3/31"
format: docx
editor: visual
echo: false
---

# Library

```{r}
library(DescTools)
library(dplyr)
library(tidyr)
library(tidyverse)
library(here)
library(pastecs)
library(naniar)
```

# Load data

```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "APHA","Data", "cleandata", "April11.rds")
Jan_March = readRDS(data_location)

```

# Creating a data set that includes data January 1st, 2023 through March 31st, 2023

```{r}
Jan_March <- Jan_March[!(grepl("^10|^11|^12|^04", Jan_March$Date)), ]
```

# subsetting the data 
```{r}
my_data_subset <- Jan_March[, c(23:32)]
```

```{r}
my_data_subset <- my_data_subset %>%
  mutate(num_conditions = rowSums(!is.na(select(., starts_with("Conditions")))),
         response_group = ifelse(is.na(num_conditions), "missing",
                                 ifelse(num_conditions == 1, "at least one",
                                        ifelse(num_conditions == 2, "at least two",
                                               ifelse(num_conditions == 3, "three or more",                                                    ifelse(num_conditions == 0, "zero",
                                               "three or more"))))))
```


# summarizing the response group variable 
```{r}
response_group = my_data_subset$response_group

response_group_pertable= PercTable(response_group)
response_group_pertable
```

# break down of those who had covid in household
## reloading 
```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "APHA","Data", "cleandata", "April11.rds")
Jan_March = readRDS(data_location)

Jan_March <- Jan_March[!(grepl("^10|^11|^12|^04", Jan_March$Date)), ]
```

#Selecting only those who answered yes to having covid in the household
```{r}
my_data_yes <- subset(Jan_March, Question_1 == "Yes")
```

# Summary for gender

```{r}
Gender = my_data_yes$Gender %>% replace(is.na(.), "*")

Gender_pertable= PercTable(Gender)
Gender_pertable

```

# Summary for race

```{r}
#changes NA values to missing 
race = my_data_yes$Race_Ethnicity %>% replace(is.na(.), "*")

race_pertable= PercTable(race)
race_pertable

```

# Summary for Income

```{r}
Income = my_data_yes$Income %>% replace(is.na(.), "*")

Income_pertable= PercTable(Income)
Income_pertable

```

# Summary for age

```{r}
#changes NA values to missing 
Age = my_data_yes$Age %>% replace(is.na(.), "*")

Age_pertable= PercTable(Age)
Age_pertable
```

# Summary for Question_13: Did your children or your family member experience Fever or chills

```{r}
Question_13_Fever = my_data_yes$Question_13_Fever %>% replace(is.na(.), "*")

Question_13_Fever_pertable= PercTable(Question_13_Fever)
Question_13_Fever_pertable
```

# Summary for Question_13_Cough: Did your children or your family member experience cough

```{r}
Question_13_Cough = my_data_yes$Question_13_Cough %>% replace(is.na(.), "*")

Question_13_Cough_pertable= PercTable(Question_13_Cough)
Question_13_Cough_pertable
```

# Summary for Question_13_Shortness_of_breath: Did your children or your family member experience Shortness_of_breath

```{r}
Question_13_Shortness_of_breath = my_data_yes$Question_13_Shortness_of_breath %>% replace(is.na(.), "*")

Question_13_Shortness_of_breath_pertable= PercTable(Question_13_Shortness_of_breath)
Question_13_Shortness_of_breath_pertable
```

# Summary for Question_13_Fatigue: Did your children or your family member experience Fatigue

```{r}
Question_13_Fatigue = my_data_yes$Question_13_Fatigue %>% replace(is.na(.), "*")

Question_13_Fatigue_pertable= PercTable(Question_13_Fatigue)
Question_13_Fatigue_pertable

```

# Summary for Question_13_Muscle_Body_Aches: Did your children or your family member experience \_Muscle_Body_Aches

```{r}
Question_13_Muscle_Body_Aches = my_data_yes$Question_13_Muscle_Body_Aches %>% replace(is.na(.), "*")

Question_13_Muscle_Body_Aches_pertable= PercTable(Question_13_Muscle_Body_Aches)
Question_13_Muscle_Body_Aches_pertable
```

# Summary for Question_13_Headache: Did your children or your family member experience Headache

```{r}
Question_13_Headache = my_data_yes$Question_13_Headache %>% replace(is.na(.), "*")

Question_13_Headache_pertable= PercTable(Question_13_Headache)
Question_13_Headache_pertable
```

# Summary for Question_13_Loss_of_Taste: Did your children or your family member experience Loss_of_Taste

```{r}
Question_13_Loss_of_Taste = my_data_yes$Question_13_Loss_of_Taste %>% replace(is.na(.), "*")

Question_13_Loss_of_Taste_pertable= PercTable(Question_13_Loss_of_Taste)
Question_13_Loss_of_Taste_pertable
```

# Summary for Question_13_Sore_Throat: Did your children or your family member experience Sore_Throat

```{r}
Question_13_Sore_Throat = my_data_yes$Question_13_Sore_Throat %>% replace(is.na(.), "*")

Question_13_Sore_Throat_pertable= PercTable(Question_13_Sore_Throat)
Question_13_Sore_Throat_pertable
```

# Summary for Question_13_Congestion: Did your children or your family member experience Congestion

```{r}
Question_13_Congestion = my_data_yes$Question_13_Congestion %>% replace(is.na(.), "*")

Question_13_Congestion_pertable= PercTable(Question_13_Congestion)
Question_13_Congestion_pertable
```

# Summary for Question_13_Nausea: Did your children or your family member experience Nausea

```{r}
Question_13_Nausea = my_data_yes$Question_13_Nausea %>% replace(is.na(.), "*")

Question_13_Nausea_pertable= PercTable(Question_13_Nausea)
Question_13_Nausea_pertable
```

# Summary for Question_13_Diarrhea: Did your children or your family member experience Diarrhea

```{r}
Question_13_Diarrhea = my_data_yes$Question_13_Diarrhea %>% replace(is.na(.), "*")

Question_13_Diarrhea_pertable= PercTable(Question_13_Diarrhea)
Question_13_Diarrhea_pertable
```

# Summary for Question_13_Asymptomatic: Did your children or your family member experience Asymptomatic

```{r}
Question_13_Asymptomatic = my_data_yes$Question_13_Asymptomatic %>% replace(is.na(.), "*")

Question_13_Asymptomatic_pertable= PercTable(Question_13_Asymptomatic)
Question_13_Asymptomatic_pertable
```

# Summary for Question_13_Other: Did your children or your family member experience other

```{r}
Question_13_Other = my_data_yes$Question_13_Other %>% replace(is.na(.), "*")

Question_13_Other_pertable= PercTable(Question_13_Other)
Question_13_Other_pertable
```

# Summary for Question_14: Describe your symptoms

```{r}
Question_14 = my_data_yes$Question_14 %>% replace(is.na(.), "*")

Question_14_pertable= PercTable(Question_14)
Question_14_pertable
```

