---
title: "Quarterly Report for HC_HIT-01, HC_HIT-02 and HC_HIT-03"
format: docx
editor: visual
echo: false
---
# Library

```{r}
library(DescTools)
library(tidyr)
library(tidyverse)
library(here)
library(pastecs)
library(naniar)
library(readxl)
library(Hmisc)
library(dplyr)
library(gtsummary)
```

# Load data

```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "APHA","Data", "cleandata", "April11.rds")
Jan_March = readRDS(data_location)

```

# Creating a data set that includes data January 1st, 2023 through March 31st, 2023

```{r}
Jan_March <- Jan_March[!(grepl("^10|^11|^12|^04", Jan_March$Date)), ]
```


## Current project data related to Healthy People 2030 objectives: HC/HIT-01

Question_32: "Did the information provider during the event today check your understanding of the COVID-19 health information provided including information about the?"

```{r}
#getting a count for our indicator PM #5 HC-HIT 01  
Q32 = Jan_March$Question_32

#replacing NA values with *
Q32 = Q32 %>% replace(is.na(.), "*")

Q32_pertable= PercTable(Q32)
Q32_pertable
```

## Current project data related to Healthy People 2030 objectives: HC/HIT-02

Question 33: "Were you satisfied with the communication regarding COVID-19 health information including information about the vaccine during the event today?"

```{r}
#getting a count for our indicator PM #5 HC-HIT 01  
Q33 = Jan_March$Question_33

#replacing NA values with *
Q33 = Q33 %>% replace(is.na(.), "*")

Q33_pertable= PercTable(Q33)
Q33_pertable
```

## Current project data related to Healthy People 2030 objectives: HC/HIT-03

Question 34: "Were you involved in decisions regarding COVID-19 vaccination decisions made today?"

```{r}
#getting a count for our indicator PM #5 HC-HIT 01  
Q34 = Jan_March$Question_34

#replacing NA values with *
Q34 = Q34 %>% replace(is.na(.), "*")

Q34_pertable= PercTable(Q34)
Q34_pertable
```
