# Cleaning file for the statistical analysis investigating the association between Covid-19 exposure and symptom severity with vaccination status or intent 

## Library 
```{r}
library(here)
library(readxl)
```


## Loading the clean data 
```{r}
#importing the file with surveys up until Feb 28th 
location = here("Primary Data Analysis ASU","APHA", "Data", "cleandata", "March25.rds")

#naming the rawdata 
asu_merged = readRDS(location)
```


## Cleaning the exposed questions: changing all values that follow question 1(Q2.1) if this question was completed as either: no, not sure or do not know then mark Question 2 - Question 14 as missing 
```{r}
asu_merged$Question_2[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_3[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_4[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_5[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_6[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_7[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_8[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_9[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_10[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_11[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_12[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Fever[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Cough[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Shortness_of_breath[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Fatigue[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Muscle_Body_Aches[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Headache[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Loss_of_Taste[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Sore_Throat[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Congestion[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Nausea[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Diarrhea[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Asymptomatic[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_13_Other[asu_merged$Question_1 > 1 ] <- "*"
asu_merged$Question_14[asu_merged$Question_1 > 1 ] <- "*"

#changing the values to symptoms questions to missing if answered "yes" to being asymptomatic 
asu_merged$Question_13_Fever[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Cough[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Shortness_of_breath[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Fatigue[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Muscle_Body_Aches[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Headache[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Loss_of_Taste[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Sore_Throat[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Congestion[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Nausea[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
asu_merged$Question_13_Diarrhea[asu_merged$Question_13_Asymptomatic == 1 ] <- "*"
```


## Subsetting the survey in order to just contain symptom questions
```{r}
exposed <- subset(asu_merged, select = c(Question_1, Question_13_Fever:Question_13_Other, Question_15, Question_27))
```

## Checking the varibale types 
```{r}
str(exposed)
```

## All Variables are saved as character variables so lets convert them to numeric variables 
```{r}
# Converting variables from character variables to numeric variables 
exposed$Question_1 <- as.numeric(exposed$Question_1)
exposed$Question_13_Fever <- as.numeric(exposed$Question_13_Fever)
exposed$Question_13_Cough <- as.numeric(exposed$Question_13_Cough)
exposed$Question_13_Shortness_of_breath <- as.numeric(exposed$Question_13_Shortness_of_breath)
exposed$Question_13_Fatigue <- as.numeric(exposed$Question_13_Fatigue)
exposed$Question_13_Muscle_Body_Aches <- as.numeric(exposed$Question_13_Muscle_Body_Aches)
exposed$Question_13_Headache <- as.numeric(exposed$Question_13_Headache)
exposed$Question_13_Loss_of_Taste <- as.numeric(exposed$Question_13_Loss_of_Taste)
exposed$Question_13_Sore_Throat <- as.numeric(exposed$Question_13_Sore_Throat)
exposed$Question_13_Congestion <- as.numeric(exposed$Question_13_Congestion)
exposed$Question_13_Nausea <- as.numeric(exposed$Question_13_Nausea)
exposed$Question_13_Diarrhea <- as.numeric(exposed$Question_13_Diarrhea)
exposed$Question_13_Asymptomatic <- as.numeric(exposed$Question_13_Asymptomatic)
exposed$Question_13_Other <- as.numeric(exposed$Question_13_Other)
exposed$Question_15 <- as.numeric(exposed$Question_15)
exposed$Question_27 <- as.numeric(exposed$Question_27)
```


## Removing all participants who answered No, not sure, do not know or left question 1 blank
```{r}
# Replace the special character "*" with 0
exposed[exposed == "*"] <- 0

# Replace all NA values with 0
exposed[is.na(exposed)] <- 0

#removing observations based on participants who answered no to question 1
exposed = exposed[exposed$Question_1 != "2", ]

#removing observations based on participants who answered not sure to question 1
exposed = exposed[exposed$Question_1 != "3", ]

#removing observations based on participants who answered do not know to question 1
exposed = exposed[exposed$Question_1 != "4", ]

#removing observations based on participants who did not answer question 1 
exposed = exposed[exposed$Question_1 != "0", ]

```
Now we have a data set that is 361 observations which is all of the participants who had Covid-19 or had a family member who had Covid-19. These are exposed individuals 

```{r}
counts = table(exposed$Question_15)

props = counts / length(exposed$Question_15)
```

## Removing those in the exposed group who have answered missing to question 15 since less than 5% of the exposure group answered missing 
```{r}
#removing observations based on participants who did not answer question 1 
exposed = exposed[exposed$Question_15 != "0", ]

```

## Calculating the scale mean for Question 15 
```{r}
sum_question15 = sum(exposed$Question_15)

mean_question15 = sum_question15 / 344

Sd_question_15 = sd(exposed$Question_15)
```



## Taking a look at the symptom severity of those exposed to covid-19 after participants who answered missing to question 15 were removed 
```{r}
table(exposed$Question_13_Fever)
table(exposed$Question_13_Cough)
table(exposed$Question_13_Shortness_of_breath)
table(exposed$Question_13_Fatigue)
table(exposed$Question_13_Muscle_Body_Aches)
table(exposed$Question_13_Headache)
table(exposed$Question_13_Loss_of_Taste)
table(exposed$Question_13_Sore_Throat)
table(exposed$Question_13_Congestion)
table(exposed$Question_13_Nausea)
table(exposed$Question_13_Diarrhea)
table(exposed$Question_13_Asymptomatic)
table(exposed$Question_13_Other)
```

Creating a new data frame with just asymptomatic individuals 
```{r}
asymptomatic = exposed

#removing anyone that was symptomatic 
asymptomatic = asymptomatic[asymptomatic$Question_13_Asymptomatic != "0", ]

```


## Calculating the scale mean for Question 15 for those assymptomatic individuals 
```{r}
sum_question15 = sum(asymptomatic$Question_15)

mean_question15 = sum_question15 / 30

Sd_question_15 = sd(asymptomatic$Question_15)
```

## Creating a new data set from the exposed individuals who are symptomatic 
```{r}
#creating data set
symptomatic = exposed

#removing asymptomatic individuals 
symptomatic = subset(symptomatic, select = c(Question_1, Question_13_Fever:Question_13_Diarrhea, Question_13_Other, Question_15, Question_27))

#creating a variable for symptomatic individuals if any of the symptom questions were answered 1 then the symptomatic question should be answered as yes 
symptomatic = exposed %>%
  mutate(symptomatic = if_else(rowSums(select(., starts_with("Question_13"))) > 0, "Yes", "No"))

#removing observations based on participants who had no to having symptoms 
symptomatic = symptomatic[symptomatic$symptomatic != "No", ] 
```

## Determining the risk score of symptomatic individuals 
```{r}
sum_question15 = sum(symptomatic$Question_15)

mean_question15 = sum_question15 / 331

Sd_question_15 = sd(symptomatic$Question_15)
```


## Unexposed group: Subsetting the survey in order to just contain symptom questions
```{r}
unexposed <- subset(asu_merged, select = c(Question_1, Question_13_Fever:Question_13_Other, Question_15, Question_27))
```

 
## Checking the varibale types 
```{r}
str(unexposed)
```

## All Variables are saved as character variables so lets convert them to numeric variables 
```{r}
# Converting variables from character variables to numeric variables 
unexposed$Question_1 <- as.numeric(unexposed$Question_1)
unexposed$Question_13_Fever <- as.numeric(unexposed$Question_13_Fever)
unexposed$Question_13_Cough <- as.numeric(unexposed$Question_13_Cough)
unexposed$Question_13_Shortness_of_breath <- as.numeric(unexposed$Question_13_Shortness_of_breath)
unexposed$Question_13_Fatigue <- as.numeric(unexposed$Question_13_Fatigue)
unexposed$Question_13_Muscle_Body_Aches <- as.numeric(unexposed$Question_13_Muscle_Body_Aches)
unexposed$Question_13_Headache <- as.numeric(unexposed$Question_13_Headache)
unexposed$Question_13_Loss_of_Taste <- as.numeric(unexposed$Question_13_Loss_of_Taste)
unexposed$Question_13_Sore_Throat <- as.numeric(unexposed$Question_13_Sore_Throat)
unexposed$Question_13_Congestion <- as.numeric(unexposed$Question_13_Congestion)
unexposed$Question_13_Nausea <- as.numeric(unexposed$Question_13_Nausea)
unexposed$Question_13_Diarrhea <- as.numeric(unexposed$Question_13_Diarrhea)
unexposed$Question_13_Asymptomatic <- as.numeric(unexposed$Question_13_Asymptomatic)
unexposed$Question_13_Other <- as.numeric(unexposed$Question_13_Other)
unexposed$Question_15 <- as.numeric(unexposed$Question_15)
unexposed$Question_27 <- as.numeric(unexposed$Question_27)
```


## Removing all participants who answered No, not sure, do not know or left question 1 blank
```{r}
# Replace the special character "*" with 0
unexposed[unexposed == "*"] <- 0

# Replace all NA values with 0
unexposed[is.na(unexposed)] <- 0

#removing observations based on participants who answered no to question 1
unexposed = unexposed[unexposed$Question_1 != "1", ]

#removing observations based on participants who answered not sure to question 1
unexposed = unexposed[unexposed$Question_1 != "3", ]

#removing observations based on participants who answered do not know to question 1
unexposed = unexposed[unexposed$Question_1 != "4", ]

#removing observations based on participants who did not answer question 1 
unexposed = unexposed[unexposed$Question_1 != "0", ]

```
Now we have a data set that is 361 observations which is all of the participants who had Covid-19 or had a family member who had Covid-19. These are unexposed individuals 

```{r}
counts2 = table(unexposed$Question_15)

props2 = counts2 / length(unexposed$Question_15)
```


## Removing those in the unexposed group who have answered missing to question 15 since less than 5% of the unexposure group answered missing 
```{r}
#removing observations based on participants who did not answer question 1 
unexposed = unexposed[unexposed$Question_15 != "0", ]

```


## Calculating the scale mean for Question 15 
```{r}
sum_question15_unexp = sum(unexposed$Question_15)

mean_question15_unexp = sum_question15 / 527

Sd_question_15_unexp = sd(unexposed$Question_15)
```



# Creating a data set with just question 1 and question 15 to test the association betweeen exposed and unexposed and percieved risk 

## Loading the clean data 
```{r}
#importing the file with survey 
location = here("Primary Data Analysis ASU","APHA", "Data", "cleandata", "asu_merged.xlsx")

#naming the rawdata 
asu_merged = read_excel(location)
```

## Subsetting the survey to contain question 1 and question 15
```{r}
exposed_unexposed <- subset(asu_merged, select = c(Question_1, Question_15))
```

## Changing data to numeric data 
```{r}
exposed_unexposed$Question_1 <- as.numeric(exposed_unexposed$Question_1)
exposed_unexposed$Question_15 <- as.numeric(exposed_unexposed$Question_15)
```


## Removing all participants who answered No, not sure, do not know or left question 1 blank
```{r}
# Replace the special character "*" with 0
exposed_unexposed[exposed_unexposed == "*"] <- 0

# Replace all NA values with 0
exposed_unexposed[is.na(exposed_unexposed)] <- 0

#taking a look at the distribution of both questions 
table(exposed_unexposed$Question_1)
table(exposed_unexposed$Question_15)

### removing those who resonded do not know and not sure to question 1 
#removing observations based on participants who answered not sure to question 1
exposed_unexposed = exposed_unexposed[exposed_unexposed$Question_1 != "3", ]

#removing observations based on participants who answered do not know to question 1
exposed_unexposed = exposed_unexposed[exposed_unexposed$Question_1 != "4", ]

#now taking a look at the distribution 
table(exposed_unexposed$Question_1)
table(exposed_unexposed$Question_15)
```

## running the chi square test with missing  
```{r}
chisq_test <- chisq.test(table(exposed_unexposed$Question_1, exposed_unexposed$Question_15))
```
indicates there is a strong association between the two questions 

## running the chi square test without missing 
```{r}
#removing observations based on participants who answered missing to question 1
exposed_unexposed = exposed_unexposed[exposed_unexposed$Question_1 != "0", ]

#removing observations based on participants who answered missing to question 1
exposed_unexposed = exposed_unexposed[exposed_unexposed$Question_15 != "0", ]

#now taking a look at the distribution 
table(exposed_unexposed$Question_1)
table(exposed_unexposed$Question_15)

chisq_test <- chisq.test(table(exposed_unexposed$Question_1, exposed_unexposed$Question_15))

```

## Creating a new variable for question 15
```{r}
# Create a new variable with "not at risk", "neutral", and "at risk" categories
Risk <- ifelse(exposed_unexposed$Question_15 %in% c(1,2), "not at risk", 
               ifelse(exposed_unexposed$Question_15 == 3, "neutral", "at risk"))
exposed_unexposed$Question_15 <- Risk
```

## making a contigency table between question 1 and question 15 
```{r}
freq_table <- table(exposed_unexposed$Question_1, exposed_unexposed$Question_15)
```

## Calculating the ORs
```{r}
exposed_at_risk = (147 / (87 + 110)) / (157 / (101 + 270))

#calculating the confidence interval 
LL_exposed_at_risk <- exp(log(exposed_at_risk) - 1.96 * sqrt(1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270))
UL_exposed_at_risk <- exp(log(exposed_at_risk) + 1.96 * sqrt((1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270)))

#calculating the standard error
SE = sqrt((1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270)))


#running fisher's test on the contingency table 
contingency_table <- matrix(c(147, 87, 110, 156, 101, 270), nrow = 2, byrow = TRUE)
fisher.test(contingency_table)


LL_exposed_at_risk
UL_exposed_at_risk

#OR for neutral 
exposed_neutral = (87 / (147 + 110)) / (101 / (156 + 270))

#calculating the confidence interval
LL_neutral <- exp(log(exposed_neutral) - 1.96 * sqrt(1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270))
UL_neutral <- exp(log(exposed_neutral) + 1.96 * sqrt((1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270)))

LL_neutral
UL_neutral

exposed_not_risk = (110 / (147 + 87)) / (270 / (156 + 101))
#calculating the confidence interval
LL_not_risk <- exp(log(exposed_not_risk) - 1.96 * sqrt(1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270))
UL_not_risk <- exp(log(exposed_not_risk) + 1.96 * sqrt((1/110 + 1/87 + 1/147 + 1/156 + 1/101 + 1/270)))

LL_not_risk
UL_not_risk
```
