# Determining alpha's Alpha for Vaccine Hesitancy and Vaccine uptake Questions

### Packages

```{r}
#library 
library(here)
library(psych) #has cronach alpha function 
library(readxl) #for reading in the excel clean data 
```

### Loading the data

```{r}
asu_merged <- read_excel(here("Primary Data Analysis ASU", "APHA", "Data", "cleandata", "asu_merged.xlsx"))
```

### Cleaning: Removing all of the special characters * which indicate missing in order to run cronbach's alpha 
```{r}
# Replace special characters * with NA in the data frame
asu_merged[asu_merged == "*" | asu_merged == "NA"] <- NA
```

### Changing questions from character variables to numerical variables 
```{r}
asu_merged <- asu_merged %>%
  mutate(across(Question_44:Question_78, as.numeric))
```


## Vaccine Hesitancy

### Subsetting Vaccine Hesitancy questions by each vaccine hesitancy barrier

#### Clincial Barriers

```{r}
#clinical barriers: Question 44 through Question 53
clincal_barriers <- subset(asu_merged, select = c(Question_44, Question_45, Question_46, Question_47, Question_48, Question_49, Question_50, Question_51, Question_52, Question_53))
```

#### Access Barriers

```{r}
#access barriers: Question 54 through Question 57
access_barriers <- subset(asu_merged, select = c(Question_54, Question_55, Question_56, Question_57))
```

#### Information Barriers

```{r}
#Information barriers: Question 58 through Question 61
information_barriers <- subset(asu_merged, select = c(Question_58, Question_59, Question_60, Question_61))
```

#### Trust Barriers

```{r}
#Trust barriers: Question 62 through Question 66
trust_barriers <- subset(asu_merged, select = c(Question_62, Question_63, Question_64, Question_65, Question_66))
```

#### Religious Barriers

```{r}
#Religious barriers: Question 67 through Question 71
religious_barriers <- subset(asu_merged, select = c(Question_67, Question_68, Question_69, Question_70, Question_70))
```

## Vaccine Uptake

### Subsetting vaccine uptake questions

```{r}
#Question 72 through Question 78 
uptake <- subset(asu_merged, select = c(Question_72, Question_73, Question_74, Question_75, Question_76, Question_77, Question_78))
```


## alpha values for Vaccine Hesitancy barriers

```{r}
#clinical 
alpha(clincal_barriers)

#access
alpha(access_barriers)

#information
alpha(information_barriers)

#trust
alpha(trust_barriers)

#religious
alpha(religious_barriers)
```
