# performing the mcar test for Vaccine Hesitancy questions and Vaccine uptake questions

### Reference for the naniar package can be found [here](https://search.r-project.org/CRAN/refmans/naniar/html/mcar_test.html)

### Reference for the misty package can be found [here](https://search.r-project.org/CRAN/refmans/misty/html/na.test.html)

### Packages

```{r}
install.packages("misty")
#library 
library(here)
library(psych) #has cronbach alpha function 
library(readxl) #for reading in the excel clean data 
library(tidyverse)
library(naniar) #mcar_test function 
library(misty) #na.test function 
```

### Loading the data

```{r}
asu_merged <- read_excel(here("Primary Data Analysis ASU", "APHA", "Data", "cleandata", "asu_merged.xlsx"))
```

### Cleaning: Removing all of the special characters \* which indicate missing in order to run cronbach's alpha

```{r}
# Replace special characters * with NA in the data frame
asu_merged[asu_merged == "*" | asu_merged == "NA"] <- NA
```

### Changing questions from character variables to numerical variables

```{r}
asu_merged <- asu_merged %>%
  mutate(across(Question_44:Question_78, as.numeric))
```

## Vaccine Hesitancy

### Subsetting Vaccine Hesitancy questions by each vaccine hesitancy barrier

#### Clinicial Barriers

```{r}
#clinical barriers: Question 44 through Question 53
clinical_barriers <- subset(asu_merged, select = c(Question_44, Question_45, Question_46, Question_47, Question_48, Question_49, Question_50, Question_51, Question_52, Question_53))

#converting to numerical variable 
clinical_barriers <- as.data.frame(apply(clinical_barriers, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(clinical_barriers)
```

#### Access Barriers

```{r}
#access barriers: Question 54 through Question 57
access_barriers <- subset(asu_merged, select = c(Question_54, Question_55, Question_56, Question_57))

#converting to numerical variable 
access_barriers <- as.data.frame(apply(access_barriers, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(access_barriers)
```

#### Information Barriers

```{r}
#Information barriers: Question 58 through Question 61
information_barriers <- subset(asu_merged, select = c(Question_58, Question_59, Question_60, Question_61))

#converting to numerical variable 
information_barriers <- as.data.frame(apply(information_barriers, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(information_barriers)
```

#### Trust Barriers

```{r}
#Trust barriers: Question 62 through Question 66
trust_barriers <- subset(asu_merged, select = c(Question_62, Question_63, Question_64, Question_65, Question_66))

#converting to numerical variable 
trust_barriers <- as.data.frame(apply(trust_barriers, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(trust_barriers)
```

#### Religious Barriers

```{r}
#Religious barriers: Question 67 through Question 71
religious_barriers <- subset(asu_merged, select = c(Question_67, Question_68, Question_69, Question_70, Question_71))

#converting to numerical variable 
religious_barriers <- as.data.frame(apply(religious_barriers, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(religious_barriers)
```

## Vaccine Uptake

### Subsetting vaccine uptake questions

```{r}
#Question 72 through Question 78 
uptake <- subset(asu_merged, select = c(Question_72, Question_73, Question_74, Question_75, Question_76, Question_77, Question_78))

#converting to numerical variable 
uptake <- as.data.frame(apply(uptake, 2, as.numeric)) 

#check if changing to a numerical variable worked 
str(uptake)
```

### Null Hypothesis for Little's Missing Completely at Random Test

```{r}
# Null = the missing data is missing completely at random 
```

### MCAR test for clinical_barriers

```{r}
#running the MCAR test from two different packages for 
mcar_test(clinical_barriers) 
na.test(clinical_barriers)
```

Results:

-   chi square test value: 381.80: measures the degree of discrepancy between the observed missing data pattern and the expected missing data pattern under the assumption of MCAR. So a high value of 381.80 would indicate high discrepancy or difference between the observed data pattern and the expected data pattern.

-   p-value of < 0.05 indicates that the data is not missing completely at random

-   Moving forward: we will have to treat clinical barrier variables either as missing at random or missing not at random

### MCAR test for Access Barriers

```{r}
#running the MCAR test from two different packages for 
mcar_test(access_barriers) 
na.test(access_barriers)
```

Results:

-   chi square test value: 28.19 is small which indicates not a lot of difference between the observed data pattern and the expected data pattern.

-   p-value > 0.05 so we can fail to reject the null indicating that the access barrier variables can be treated as missing completely at random

-   Moving forward: we can go ahead and run the cronbach test of reliability even though missing is present

### MCAR test for Information Barriers

```{r}
#running the MCAR test from two different packages for 
mcar_test(information_barriers) 
na.test(information_barriers)
```

Results:

-   chi square test value: 29.07 is small which indicates not a lot of difference between the observed data pattern and the expected data pattern.

-   p-value > 0.05 so we can fail to reject the null indicating that the access barrier variables can be treated as missing completely at random

-   Moving forward: we can go ahead and run the cronbach test of reliability even though missing is present

### MCAR test for Trust Barriers

```{r}
#running the MCAR test from two different packages for 
mcar_test(trust_barriers) 
na.test(trust_barriers)
```

-   chi square test value: 29.07 is small which indicates not a lot of difference between the observed data pattern and the expected data pattern.

-   p-value = 0.05 so we can fail to reject the null indicating that the access barrier variables can be treated as missing completely at random

-   Moving forward: we can go ahead and run the cronbach test of reliability even though missing is present

### MCAR test for Religious Barriers

```{r}
#running the MCAR test from two different packages for 
mcar_test(religious_barriers) 
na.test(religious_barriers)
```

Results:

-   chi square test value: 60.21:

-   p-value of < 0.05 indicates that the data is not missing completely at random

-   Moving forward: we will have to treat clinical barrier variables either as missing at random or missing not at random

### MCAR test for vaccine uptake 

```{r}
#running the MCAR test from two different packages for 
mcar_test(uptake) 
na.test(uptake)
```

Results:

-   chi square test value: 179.80

-   p-value of < 0.05 indicates that the data is not missing completely at random

-   Moving forward: we will have to treat clinical barrier variables either as missing at random or missing not at random