#cleaning in preparation for descriptive summary of data

#library for code
```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(data.table)
library(stringi)
library(Hmisc)
library(ggplot2)
library(DescTools)
library(here)
```

#importing the data  
```{r}
location = here("Primary Data Analysis", "APHA_Data_CutOff", "Clean_Data", "asu_merged.xlsx")

#naming the rawdata 
asu_merged = read_excel(location)

#removing the space from the Health_Insurance variable name 
colnames(asu_merged)[which(names(asu_merged) == "Health Insurance")] <- "Health_Insurance"

#coping the data set and identifying it by the date it was merged 
June15th = asu_merged

#note that june15th refers to when you wrote the code. the data is from november-april
```

#data qualtiy cleaning
```{r}
#changing all values to missing of Number_of_children_1, Number_of_children_2 and Number_of_children_3 when Children was answered "No" (2)
May17th$Number_children_1[May17th$Children == 2 ] <- "*"
May17th$Number_children_2[May17th$Children == 2 ] <- "*"
May17th$Number_children_3[May17th$Children == 2 ] <- "*"

#changing all values to missing of Number_elderly_1, Number_elderly_2 Elderly_family was answered "No" (2)
May17th$Number_elderly_1[May17th$Elderly_family == 2 ] <- "*"
May17th$Number_elderly_2[May17th$Elderly_family == 2 ] <- "*"

#changing all values that follow question 1(Q2.1) if this question was completed as either: no, not sure or do not know then mark Question 2 - Question 14 as missing 
May17th$Question_2[May17th$Question_1 > 1 ] <- "*"
May17th$Question_3[May17th$Question_1 > 1 ] <- "*"
May17th$Question_4[May17th$Question_1 > 1 ] <- "*"
May17th$Question_5[May17th$Question_1 > 1 ] <- "*"
May17th$Question_6[May17th$Question_1 > 1 ] <- "*"
May17th$Question_7[May17th$Question_1 > 1 ] <- "*"
May17th$Question_8[May17th$Question_1 > 1 ] <- "*"
May17th$Question_9[May17th$Question_1 > 1 ] <- "*"
May17th$Question_10[May17th$Question_1 > 1 ] <- "*"
May17th$Question_11[May17th$Question_1 > 1 ] <- "*"
May17th$Question_12[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Fever[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Cough[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Shortness_of_breath[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Fatigue[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Muscle_Body_Aches[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Headache[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Loss_of_Taste[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Sore_Throat[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Congestion[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Nausea[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Diarrhea[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Asymptomatic[May17th$Question_1 > 1 ] <- "*"
May17th$Question_13_Other[May17th$Question_1 > 1 ] <- "*"
May17th$Question_14[May17th$Question_1 > 1 ] <- "*"

#If question 22 (3.1) was reported as No, Not Sure or do not know then question 23 (3.2) should be reported as missing 
May17th$Question_23[May17th$Question_22 > 1 ] <- "*"

#If question 25 (3.7) was reported as yes then Question 27 (were you vaccinated in the past), Question 28 (Do you plan to get vaccinated in the near future) and Question 29 (If/When you decide to get vaccinated, do you know where to get a vaccine) should all be missing 
May17th$Question_27[May17th$Question_25 == 1 ] <- "*"
May17th$Question_28[May17th$Question_25 == 1 ] <- "*"
May17th$Question_29[May17th$Question_25 == 1 ] <- "*"

#If question 25 was reported as no then question 26 (was this your first dose) should be reported as missing 
May17th$Question_26[May17th$Question_25 > 1 ] <- "*"

#if question 27(were you vaccinated in the past) was answered yes then question 28(Do you plan to get vaccinated in the near future) and Question 29 (If/When you decide to get vaccinated, do you know where to get a vaccine) should be missing 
May17th$Question_28[May17th$Question_27 == 1 ] <- "*"
May17th$Question_29[May17th$Question_27 == 1 ] <- "*"

#if question 40 (did your child or children also get the vaccine today?) was reported as yes then question 42 (was your child vaccinated in the past) and question 43 (do you plan to get your child vaccinated in the near future) should both be missing 
May17th$Question_42[May17th$Question_40 == 1 ] <- "*"
May17th$Question_43[May17th$Question_40 == 1 ] <- "*"

#if question 40 was reported as no or as "I do not have children under 18 in my household" then question 41 (was the dose your child received their first dose)should be missing 
May17th$Question_41[May17th$Question_40 > 1 ] <- "*"

#if question 42 was reported as yes then question 43 should be missing 
May17th$Question_43[May17th$Question_42 == 1 ] <- "*"

#if a respondent responded yes to having a condition then all of then they should report missing to the no conditions question 
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Cancer == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Severe_Allergies == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Seizures == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Obesity == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Cardio_Disease == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Rheumatological == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Pulmonary == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Diabetes == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Immuno == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Pregnancy == 1 ] <- "*"
asu_merged$Conditions_No_Conditions[asu_merged$Conditions_Other == 1 ] <- "*"

# vice versa, if a respondent responed yes to having no conditions then all of the conditions questions besides no conditions should be missing 
asu_merged$Conditions_Cancer[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Severe_Allergies[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Seizures[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Obesity[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Cardio_Disease[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Rheumatological[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Pulmonary[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Diabetes[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Immuno[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Pregnancy[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
asu_merged$Conditions_Other[asu_merged$Conditions_No_Conditions == 1 ] <- "*"
```

#changing numeric responses to characters for data summary
##potentially don't need this section but keeping for now just in case 
```{r}
#doing this so we do not have to turn to the code book for interpretation

##Gender
May17th$Gender <- ifelse(May17th$Gender == 1, "Male", 
                       ifelse(May17th$Gender == 2, "Female",
                              ifelse(May17th$Gender == 3, "I would rather not specify", NA)))

##Age
May17th$Age <- ifelse(May17th$Age == 1, "18-24 years old", 
                                 ifelse(May17th$Age == 2, "25-34 years old",
                                        ifelse(May17th$Age == 3, "35-46 years old",
                                               ifelse(May17th$Age == 4, "45-54 years old",
                                                      ifelse(May17th$Age == 5, "55-64 years old",
                                                             ifelse(May17th$Age == 6, "65-74 years old",
                                                                    ifelse(May17th$Age == 7, "75 years or older", NA)))))))
##Race_Ethnicity
May17th$Race_Ethnicity <- ifelse(May17th$Race_Ethnicity == 1, "African American", 
                                            ifelse(May17th$Race_Ethnicity == 2, "Caucasian",
                                                   ifelse(May17th$Race_Ethnicity == 3, "Latino or Hispanic",
                                                          ifelse(May17th$Race_Ethnicity == 4, "Asian",
                                                                 ifelse(May17th$Race_Ethnicity == 5, "Native American",
                                                                        ifelse(May17th$Race_Ethnicity == 6, "Other", NA))))))

##Education
May17th$Education <- ifelse(May17th$Education == 1, "Less than High School", 
                          ifelse(May17th$Education == 2, "High School",
                                 ifelse(May17th$Education == 3, "Bachelor's Degree or higher", NA)))

##Language
May17th$Language <- ifelse(May17th$Language == 1, "English", 
                         ifelse(May17th$Language == 2, "Spanish",
                                ifelse(May17th$Language == 3, "Other", NA)))
##Income
May17th$Income <- ifelse(May17th$Income == 1, "Less than $25,000", 
                       ifelse(May17th$Income == 2, "$25,000-$50,000",
                              ifelse(May17th$Income == 3, "$50,000-$100,000",
                                     ifelse(May17th$Income == 4, "More than $100,000", NA))))

##Family_household
May17th$Family_household <- ifelse(May17th$Family_household == 1, 1, 
                                 ifelse(May17th$Family_household == 2, 2,
                                        ifelse(May17th$Family_household == 3, 3,
                                               ifelse(May17th$Family_household == 4, 4,
                                                      ifelse(May17th$Family_household == 5, "5 or more", NA)))))
##Children
May17th$Children <- ifelse(May17th$Children == 1, "Yes", 
                         ifelse(May17th$Children == 2, "No", NA))
##Elderly_family
May17th$Elderly_family <- ifelse(May17th$Elderly_family == 1, "Yes", 
                               ifelse(May17th$Elderly_family == 2, "No", NA))
##Health_Insurance
May17th$Health_Insurance <- ifelse(May17th$Health_Insurance == 1, "Medicaid", 
                                                ifelse(May17th$Health_Insurance == 2, "Medicare",
                                                       ifelse(May17th$Health_Insurance == 3, "Affordable Care Act (Obamacare)",
                                                              ifelse(May17th$Health_Insurance == 4, "Uninsured",
                                                                     ifelse(May17th$Health_Insurance == 5, "Private Health_Insurance",
                                                                            ifelse(May17th$Health_Insurance == 6, "Other",
                                                                                   ifelse(May17th$Health_Insurance == 7, "Don't Know / Not Sure", NA)))))))
##Conditions_Cancer
May17th$Conditions_Cancer <- ifelse(May17th$Conditions_Cancer == 1, "Yes", NA)

##Conditions_Severe_Allergies
May17th$Conditions_Severe_Allergies <- ifelse(May17th$Conditions_Severe_Allergies == 1, "Yes", NA)

##Conditions_Seizures
May17th$Conditions_Seizures <- ifelse(May17th$Conditions_Seizures == 1, "Yes", NA)

##Conditions_Obesity
May17th$Conditions_Obesity <- ifelse(May17th$Conditions_Obesity == 1, "Yes", NA)

##Conditions_Cardio_Disease
May17th$Conditions_Cardio_Disease <- ifelse(May17th$Conditions_Cardio_Disease == 1, "Yes", NA)

##Conditions_Rheumatological
May17th$Conditions_Rheumatological <- ifelse(May17th$Conditions_Rheumatological == 1, "Yes", NA)

##Conditions_Pulmonary
May17th$Conditions_Pulmonary <- ifelse(May17th$Conditions_Pulmonary == 1, "Yes", NA)

##Conditions_Diabetes
May17th$Conditions_Diabetes <- ifelse(May17th$Conditions_Diabetes == 1, "Yes", NA)

##Conditions_Immuno
May17th$Conditions_Immuno <- ifelse(May17th$Conditions_Immuno == 1, "Yes", NA)

##Conditions_Pregnancy
May17th$Conditions_Pregnancy <- ifelse(May17th$Conditions_Pregnancy == 1, "Yes", NA)

##Conditions_Other
May17th$Conditions_Other <- ifelse(May17th$Conditions_Other == 1, "Yes", NA)

##Conditions_No_Conditions
May17th$Conditions_No_Conditions <- ifelse(May17th$Conditions_No_Conditions == 1, "Yes", NA)

##Question_1
May17th$Question_1 <- ifelse(May17th$Question_1 == 1, "Yes", 
                           ifelse(May17th$Question_1 == 2, "No",
                                  ifelse(May17th$Question_1 == 3, "Not sure",
                                         ifelse(May17th$Question_1 == 4, "Do not know", NA))))
##Question_13_Fever
May17th$Question_13_Fever <- ifelse(May17th$Question_13_Fever == 1, "Yes", NA)

##Question_13_Cough
May17th$Question_13_Cough <- ifelse(May17th$Question_13_Cough == 1, "Yes", NA)

##Question_13_Shortness_of_breath
May17th$Question_13_Shortness_of_breath <- 
  ifelse(May17th$Question_13_Shortness_of_breath == 1, "Yes", NA)

##Question_13_Fatigue
May17th$Question_13_Fatigue <- 
  ifelse(May17th$Question_13_Fatigue == 1, "Yes", NA)

##Question_13_Muscle_Body_Aches
May17th$Question_13_Muscle_Body_Aches <- 
  ifelse(May17th$Question_13_Muscle_Body_Aches == 1, "Yes", NA)

##Question_13_Headache
May17th$Question_13_Headache <- 
  ifelse(May17th$Question_13_Headache == 1, "Yes", NA)

##Question_13_Loss_of_Taste
May17th$Question_13_Loss_of_Taste <- 
  ifelse(May17th$Question_13_Loss_of_Taste == 1, "Yes", NA)

##Question_13_Sore_Throat
May17th$Question_13_Sore_Throat <- 
  ifelse(May17th$Question_13_Sore_Throat == 1, "Yes", NA)

##Question_13_Congestion
May17th$Question_13_Congestion <- 
  ifelse(May17th$Question_13_Congestion == 1, "Yes", NA)

##Question_13_Nausea
May17th$Question_13_Nausea <- 
  ifelse(May17th$Question_13_Nausea == 1, "Yes", NA)

##Question_13_Diarrhea
May17th$Question_13_Diarrhea <- 
  ifelse(May17th$Question_13_Diarrhea == 1, "Yes", NA)

##Question_13_Asymptomatic
May17th$Question_13_Asymptomatic <- 
  ifelse(May17th$Question_13_Asymptomatic == 1, "Yes", NA)

##Question_13_Other
May17th$Question_13_Other <- 
  ifelse(May17th$Question_13_Other == 1, "Yes", NA)

##Question_15
May17th$Question_15 <- ifelse(May17th$Question_15 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_15 == 2, "Disagree",
                                   ifelse(May17th$Question_15 == 3, "Neutral",
                                          ifelse(May17th$Question_15 == 4, "Agree",
                                                 ifelse(May17th$Question_15 == 5, "Strongly Agree", NA)))))
##Question_16
May17th$Question_16 <- ifelse(May17th$Question_16 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_16 == 2, "Disagree",
                                   ifelse(May17th$Question_16 == 3, "Neutral",
                                          ifelse(May17th$Question_16 == 4, "Agree",
                                                 ifelse(May17th$Question_16 == 5, "Strongly Agree", NA)))))
##Question_17
May17th$Question_17 <- ifelse(May17th$Question_17 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_17 == 2, "Disagree",
                                   ifelse(May17th$Question_17 == 3, "Neutral",
                                          ifelse(May17th$Question_17 == 4, "Agree",
                                                 ifelse(May17th$Question_17 == 5, "Strongly Agree", NA)))))
##Question_18
May17th$Question_18 <- ifelse(May17th$Question_18 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_18 == 2, "Disagree",
                                   ifelse(May17th$Question_18 == 3, "Neutral",
                                          ifelse(May17th$Question_18 == 4, "Agree",
                                                 ifelse(May17th$Question_18 == 5, "Strongly Agree", NA)))))
##Question_19
May17th$Question_19 <- ifelse(May17th$Question_19 == 1, "Yes", 
                            ifelse(May17th$Question_19 == 2, "No",
                                   ifelse(May17th$Question_19 == 3, "Not sure",
                                          ifelse(May17th$Question_19 == 4, "Do not know", NA))))
##Question_20_Basic_Health 
May17th$Question_20_Basic_Health <- 
  ifelse(May17th$Question_20_Basic_Health == 1, "Yes", NA)

##Question_20_COVID_19_Vacc 
May17th$Question_20_COVID_19_Vacc <- 
  ifelse(May17th$Question_20_COVID_19_Vacc == 1, "Yes", NA)

##Question_20_Improving_ventilation 
May17th$Question_20_Improving_ventilation <- 
  ifelse(May17th$Question_20_Improving_ventilation == 1, "Yes", NA)

##Question_20_Getting_tested 
May17th$Question_20_Getting_tested <- 
  ifelse(May17th$Question_20_Getting_tested == 1, "Yes", NA)

##Question_20_Following_recommendations
May17th$Question_20_Following_recommendations <- 
  ifelse(May17th$Question_20_Following_recommendations == 1, "Yes", NA)

##Question_20_Staying_home
May17th$Question_20_Staying_home <- 
  ifelse(May17th$Question_20_Staying_home == 1, "Yes", NA)

##Question_20_Seeking
May17th$Question_20_Seeking <- 
  ifelse(May17th$Question_20_Seeking == 1, "Yes", NA)

##Question_20_Avoiding
May17th$Question_20_Avoiding <- 
  ifelse(May17th$Question_20_Avoiding == 1, "Yes", NA)

##Question_21
May17th$Question_21 <- ifelse(May17th$Question_21 == 1, "Yes", 
                            ifelse(May17th$Question_21 == 2, "No",
                                   ifelse(May17th$Question_21 == 3, "Not sure",
                                          ifelse(May17th$Question_21 == 4, "Do not know", NA))))
##Question_22
May17th$Question_22 <- ifelse(May17th$Question_22 == 1, "Yes", 
                            ifelse(May17th$Question_22 == 2, "No",
                                   ifelse(May17th$Question_22 == 3, "Not sure",
                                          ifelse(May17th$Question_22 == 4, "Do not know", NA))))
##Question_23
May17th$Question_23 <- ifelse(May17th$Question_23 == 1, "Yes", 
                            ifelse(May17th$Question_23 == 2, "No",
                                   ifelse(May17th$Question_23 == 3, "Not sure",
                                          ifelse(May17th$Question_23 == 4, "Do not know", NA))))
##Question_24
May17th$Question_24 <- ifelse(May17th$Question_24 == 1, "Yes", 
                            ifelse(May17th$Question_24 == 2, "No",
                                   ifelse(May17th$Question_24 == 3, "Not sure",
                                          ifelse(May17th$Question_24 == 4, "Do not know", NA))))
##Question_25
May17th$Question_25 <- ifelse(May17th$Question_25 == 1, "Yes", 
                            ifelse(May17th$Question_25 == 2, "No", NA))

##Question_26
May17th$Question_26 <- ifelse(May17th$Question_26 == 1, "Yes", 
                            ifelse(May17th$Question_26 == 2, "No", NA))

##Question_27
May17th$Question_27 <- ifelse(May17th$Question_27 == 1, "Yes", 
                            ifelse(May17th$Question_27 == 2, "No", NA))

##Question_28
May17th$Question_28 <- ifelse(May17th$Question_28 == 1, "Yes", 
                            ifelse(May17th$Question_28 == 2, "No",
                                   ifelse(May17th$Question_28 == 3, "Not sure",
                                          ifelse(May17th$Question_28 == 4, "Do not know", NA))))

##Question_29
May17th$Question_29 <- ifelse(May17th$Question_29 == 1, "Yes", 
                            ifelse(May17th$Question_29 == 2, "No", NA))

##Question_30_Physician
May17th$Question_30_Physician <- 
  ifelse(May17th$Question_30_Physician == 1, "Yes", NA)

##Question_30_Nurse_Practitioner
May17th$Question_30_Nurse_Practitioner <- 
  ifelse(May17th$Question_30_Nurse_Practitioner == 1, "Yes", NA)

##Question_30_Registered_Nurse
May17th$Question_30_Registered_Nurse <- 
  ifelse(May17th$Question_30_Registered_Nurse == 1, "Yes", NA)

##Question_30_Community_Health_Advocate
May17th$Question_30_Community_Health_Advocate <- 
  ifelse(May17th$Question_30_Community_Health_Advocate == 1, "Yes", NA)

##Question_30_Community_Member
May17th$Question_30_Community_Member <- 
  ifelse(May17th$Question_30_Community_Member == 1, "Yes", NA)

##Question_30_Other
May17th$Question_30_Other <- 
  ifelse(May17th$Question_30_Other == 1, "Yes", NA)

##Question_32
May17th$Question_32 <- ifelse(May17th$Question_32 == 1, "Yes", 
                            ifelse(May17th$Question_32 == 2, "No",
                                   ifelse(May17th$Question_32 == 3, "Not sure",
                                          ifelse(May17th$Question_32 == 4, "Do not know", NA))))

##Question_33
May17th$Question_33 <- ifelse(May17th$Question_33 == 1, "Yes", 
                            ifelse(May17th$Question_33 == 2, "No",
                                   ifelse(May17th$Question_33 == 3, "Not sure",
                                          ifelse(May17th$Question_33 == 4, "Do not know", NA))))

##Question_34
May17th$Question_34 <- ifelse(May17th$Question_34 == 1, "Yes", 
                            ifelse(May17th$Question_34 == 2, "No",
                                   ifelse(May17th$Question_34 == 3, "Not sure",
                                          ifelse(May17th$Question_34 == 4, "Do not know", NA))))

##Question_35
May17th$Question_35 <- ifelse(May17th$Question_35 == 1, "Very confident", 
                            ifelse(May17th$Question_35 == 2, "Moderately confident",
                                   ifelse(May17th$Question_35 == 3, "Moderately unconfident",
                                          ifelse(May17th$Question_35 == 4, "Very unconfident", NA))))

##Question_36
May17th$Question_36 <- ifelse(May17th$Question_36 == 1, "local church", 
                                         ifelse(May17th$Question_36 == 2, "local hospital",
                                                ifelse(May17th$Question_36 == 3, "local barbershop",
                                                       ifelse(May17th$Question_36 == 4, "mobile vaccine and/or testing clinics",
                                                              ifelse(May17th$Question_36 == 5,  "other community event", NA)))))
##Question_38_Handout_flier
May17th$Question_38_Handout_flier <- 
  ifelse(May17th$Question_38_Handout_flier == 1, "Yes", NA)

##Question_38_Social_media
May17th$Question_38_Social_media <- 
  ifelse(May17th$Question_38_Social_media == 1, "Yes", NA)

##Question_38_Standard_media
May17th$Question_38_Standard_media <- 
  ifelse(May17th$Question_38_Standard_media == 1, "Yes", NA)

##Question_38_Community_Health_Advocate
May17th$Question_38_Community_Health_Advocate <- 
  ifelse(May17th$Question_38_Community_Health_Advocate == 1, "Yes", NA)

##Question_38_Church_service
May17th$Question_38_Church_service <- 
  ifelse(May17th$Question_38_Church_service == 1, "Yes", NA)

##Question_38_Barbershop
May17th$Question_38_Barbershop <- 
  ifelse(May17th$Question_38_Barbershop == 1, "Yes", NA)

##Question_38_Community_members
May17th$Question_38_Community_members <- 
  ifelse(May17th$Question_38_Community_members == 1, "Yes", NA)

##Question_38_Others
May17th$Question_38_Others <- 
  ifelse(May17th$Question_38_Others == 1, "Yes", NA)

##Question_40
May17th$Question_40 <- ifelse(May17th$Question_40 == 1, "Yes", 
                            ifelse(May17th$Question_40 == 2, "No",
                                   ifelse(May17th$Question_40 == 3, "I do not have childen under 18 in my household", NA)))

##Question_41
May17th$Question_41 <- ifelse(May17th$Question_41 == 1, "Yes", 
                            ifelse(May17th$Question_41 == 2, "No", NA))

##Question_42
May17th$Question_42 <- ifelse(May17th$Question_42 == 1, "Yes", 
                            ifelse(May17th$Question_42 == 2, "No", NA))

##Question_43
May17th$Question_43 <- ifelse(May17th$Question_43 == 1, "Yes", 
                                         ifelse(May17th$Question_43 == 2, "No",
                                                ifelse(May17th$Question_43 == 3, "Not sure",
                                                       ifelse(May17th$Question_43 == 4, "Do not know", NA))))
##Question_44
May17th$Question_44 <- ifelse(May17th$Question_44 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_44 == 2, "Disagree",
                                   ifelse(May17th$Question_44 == 3, "Neutral",
                                          ifelse(May17th$Question_44 == 4, "Agree",
                                                 ifelse(May17th$Question_44 == 5, "Strongly Agree", NA)))))
##Question_45
May17th$Question_45 <- ifelse(May17th$Question_45 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_45 == 2, "Disagree",
                                   ifelse(May17th$Question_45 == 3, "Neutral",
                                          ifelse(May17th$Question_45 == 4, "Agree",
                                                 ifelse(May17th$Question_45 == 5, "Strongly Agree", NA)))))

##Question_46
May17th$Question_46 <- ifelse(May17th$Question_46 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_46 == 2, "Disagree",
                                   ifelse(May17th$Question_46 == 3, "Neutral",
                                          ifelse(May17th$Question_46 == 4, "Agree",
                                                 ifelse(May17th$Question_46 == 5, "Strongly Agree", NA)))))

##Question_47
May17th$Question_47 <- ifelse(May17th$Question_47 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_47 == 2, "Disagree",
                                   ifelse(May17th$Question_47 == 3, "Neutral",
                                          ifelse(May17th$Question_47 == 4, "Agree",
                                                 ifelse(May17th$Question_47 == 5, "Strongly Agree", NA)))))

##Question_48
May17th$Question_48 <- ifelse(May17th$Question_48 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_48 == 2, "Disagree",
                                   ifelse(May17th$Question_48 == 3, "Neutral",
                                          ifelse(May17th$Question_48 == 4, "Agree",
                                                 ifelse(May17th$Question_48 == 5, "Strongly Agree", NA)))))

##Question_49
May17th$Question_49 <- ifelse(May17th$Question_49 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_49 == 2, "Disagree",
                                   ifelse(May17th$Question_49 == 3, "Neutral",
                                          ifelse(May17th$Question_49 == 4, "Agree",
                                                 ifelse(May17th$Question_49 == 5, "Strongly Agree", NA)))))

##Question_50
May17th$Question_50 <- ifelse(May17th$Question_50 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_50 == 2, "Disagree",
                                   ifelse(May17th$Question_50 == 3, "Neutral",
                                          ifelse(May17th$Question_50 == 4, "Agree",
                                                 ifelse(May17th$Question_50 == 5, "Strongly Agree", NA)))))

##Question_51
May17th$Question_51 <- ifelse(May17th$Question_51 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_51 == 2, "Disagree",
                                   ifelse(May17th$Question_51 == 3, "Neutral",
                                          ifelse(May17th$Question_51 == 4, "Agree",
                                                 ifelse(May17th$Question_51 == 5, "Strongly Agree", NA)))))

##Question_52
May17th$Question_52 <- ifelse(May17th$Question_52 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_52 == 2, "Disagree",
                                   ifelse(May17th$Question_52 == 3, "Neutral",
                                          ifelse(May17th$Question_52 == 4, "Agree",
                                                 ifelse(May17th$Question_52 == 5, "Strongly Agree", NA)))))

##Question_53
May17th$Question_53 <- ifelse(May17th$Question_53 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_53 == 2, "Disagree",
                                   ifelse(May17th$Question_53 == 3, "Neutral",
                                          ifelse(May17th$Question_53 == 4, "Agree",
                                                 ifelse(May17th$Question_53 == 5, "Strongly Agree", NA)))))

##Question_54
May17th$Question_54 <- ifelse(May17th$Question_54 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_54 == 2, "Disagree",
                                   ifelse(May17th$Question_54 == 3, "Neutral",
                                          ifelse(May17th$Question_54 == 4, "Agree",
                                                 ifelse(May17th$Question_54 == 5, "Strongly Agree", NA)))))

##Question_55
May17th$Question_55 <- ifelse(May17th$Question_55 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_55 == 2, "Disagree",
                                   ifelse(May17th$Question_55 == 3, "Neutral",
                                          ifelse(May17th$Question_55 == 4, "Agree",
                                                 ifelse(May17th$Question_55 == 5, "Strongly Agree", NA)))))

##Question_56
May17th$Question_56 <- ifelse(May17th$Question_56 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_56 == 2, "Disagree",
                                   ifelse(May17th$Question_56 == 3, "Neutral",
                                          ifelse(May17th$Question_56 == 4, "Agree",
                                                 ifelse(May17th$Question_56 == 5, "Strongly Agree", NA)))))

##Question_57
May17th$Question_57 <- ifelse(May17th$Question_57 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_57 == 2, "Disagree",
                                   ifelse(May17th$Question_57 == 3, "Neutral",
                                          ifelse(May17th$Question_57 == 4, "Agree",
                                                 ifelse(May17th$Question_57 == 5, "Strongly Agree", NA)))))

##Question_58
May17th$Question_58 <- ifelse(May17th$Question_58 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_58 == 2, "Disagree",
                                   ifelse(May17th$Question_58 == 3, "Neutral",
                                          ifelse(May17th$Question_58 == 4, "Agree",
                                                 ifelse(May17th$Question_58 == 5, "Strongly Agree", NA)))))

##Question_59
May17th$Question_59 <- ifelse(May17th$Question_59 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_59 == 2, "Disagree",
                                   ifelse(May17th$Question_59 == 3, "Neutral",
                                          ifelse(May17th$Question_59 == 4, "Agree",
                                                 ifelse(May17th$Question_59 == 5, "Strongly Agree", NA)))))

##Question_60
May17th$Question_60 <- ifelse(May17th$Question_60 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_60 == 2, "Disagree",
                                   ifelse(May17th$Question_60 == 3, "Neutral",
                                          ifelse(May17th$Question_60 == 4, "Agree",
                                                 ifelse(May17th$Question_60 == 5, "Strongly Agree", NA)))))

##Question_61
May17th$Question_61 <- ifelse(May17th$Question_61 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_61 == 2, "Disagree",
                                   ifelse(May17th$Question_61 == 3, "Neutral",
                                          ifelse(May17th$Question_61 == 4, "Agree",
                                                 ifelse(May17th$Question_61 == 5, "Strongly Agree", NA)))))

##Question_62
May17th$Question_62 <- ifelse(May17th$Question_62 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_62 == 2, "Disagree",
                                   ifelse(May17th$Question_62 == 3, "Neutral",
                                          ifelse(May17th$Question_62 == 4, "Agree",
                                                 ifelse(May17th$Question_62 == 5, "Strongly Agree", NA)))))

##Question_63
May17th$Question_63 <- ifelse(May17th$Question_63 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_63 == 2, "Disagree",
                                   ifelse(May17th$Question_63 == 3, "Neutral",
                                          ifelse(May17th$Question_63 == 4, "Agree",
                                                 ifelse(May17th$Question_63 == 5, "Strongly Agree", NA)))))

##Question_64
May17th$Question_64 <- ifelse(May17th$Question_64 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_64 == 2, "Disagree",
                                   ifelse(May17th$Question_64 == 3, "Neutral",
                                          ifelse(May17th$Question_64 == 4, "Agree",
                                                 ifelse(May17th$Question_64 == 5, "Strongly Agree", NA)))))

##Question_65
May17th$Question_65 <- ifelse(May17th$Question_65 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_65 == 2, "Disagree",
                                   ifelse(May17th$Question_65 == 3, "Neutral",
                                          ifelse(May17th$Question_65 == 4, "Agree",
                                                 ifelse(May17th$Question_65 == 5, "Strongly Agree", NA)))))

##Question_66
May17th$Question_66 <- ifelse(May17th$Question_66 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_66 == 2, "Disagree",
                                   ifelse(May17th$Question_66 == 3, "Neutral",
                                          ifelse(May17th$Question_66 == 4, "Agree",
                                                 ifelse(May17th$Question_66 == 5, "Strongly Agree", NA)))))

##Question_67
May17th$Question_67 <- ifelse(May17th$Question_67 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_67 == 2, "Disagree",
                                   ifelse(May17th$Question_67 == 3, "Neutral",
                                          ifelse(May17th$Question_67 == 4, "Agree",
                                                 ifelse(May17th$Question_67 == 5, "Strongly Agree", NA)))))
##Question_68
May17th$Question_68 <- ifelse(May17th$Question_68 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_68 == 2, "Disagree",
                                   ifelse(May17th$Question_68 == 3, "Neutral",
                                          ifelse(May17th$Question_68 == 4, "Agree",
                                                 ifelse(May17th$Question_68 == 5, "Strongly Agree", NA)))))
##Question_69
May17th$Question_69 <- ifelse(May17th$Question_69 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_69 == 2, "Disagree",
                                   ifelse(May17th$Question_69 == 3, "Neutral",
                                          ifelse(May17th$Question_69 == 4, "Agree",
                                                 ifelse(May17th$Question_69 == 5, "Strongly Agree", NA)))))

##Question_70
May17th$Question_70 <- ifelse(May17th$Question_70 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_70 == 2, "Disagree",
                                   ifelse(May17th$Question_70 == 3, "Neutral",
                                          ifelse(May17th$Question_70 == 4, "Agree",
                                                 ifelse(May17th$Question_70 == 5, "Strongly Agree", NA)))))
##Question_71
May17th$Question_71 <- ifelse(May17th$Question_71 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_71 == 2, "Disagree",
                                   ifelse(May17th$Question_71 == 3, "Neutral",
                                          ifelse(May17th$Question_71 == 4, "Agree",
                                                 ifelse(May17th$Question_71 == 5, "Strongly Agree", NA)))))

##Question_72
May17th$Question_72 <- ifelse(May17th$Question_72 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_72 == 2, "Disagree",
                                   ifelse(May17th$Question_72 == 3, "Neutral",
                                          ifelse(May17th$Question_72 == 4, "Agree",
                                                 ifelse(May17th$Question_72 == 5, "Strongly Agree", NA)))))

##Question_73
May17th$Question_73 <- ifelse(May17th$Question_73 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_73 == 2, "Disagree",
                                   ifelse(May17th$Question_73 == 3, "Neutral",
                                          ifelse(May17th$Question_73 == 4, "Agree",
                                                 ifelse(May17th$Question_73 == 5, "Strongly Agree", NA)))))

##Question_74
May17th$Question_74 <- ifelse(May17th$Question_74 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_74 == 2, "Disagree",
                                   ifelse(May17th$Question_74 == 3, "Neutral",
                                          ifelse(May17th$Question_74 == 4, "Agree",
                                                 ifelse(May17th$Question_74 == 5, "Strongly Agree", NA)))))

##Question_75
May17th$Question_75 <- ifelse(May17th$Question_75 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_75 == 2, "Disagree",
                                   ifelse(May17th$Question_75 == 3, "Neutral",
                                          ifelse(May17th$Question_75 == 4, "Agree",
                                                 ifelse(May17th$Question_75 == 5, "Strongly Agree", NA)))))

##Question_76
May17th$Question_76 <- ifelse(May17th$Question_76 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_76 == 2, "Disagree",
                                   ifelse(May17th$Question_76 == 3, "Neutral",
                                          ifelse(May17th$Question_76 == 4, "Agree",
                                                 ifelse(May17th$Question_76 == 5, "Strongly Agree", NA)))))

##Question_77
May17th$Question_77 <- ifelse(May17th$Question_77 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_77 == 2, "Disagree",
                                   ifelse(May17th$Question_77 == 3, "Neutral",
                                          ifelse(May17th$Question_77 == 4, "Agree",
                                                 ifelse(May17th$Question_77 == 5, "Strongly Agree", NA)))))

##Question_78
May17th$Question_78 <- ifelse(May17th$Question_78 == 1, "Strongly Disagree", 
                            ifelse(May17th$Question_78 == 2, "Disagree",
                                   ifelse(May17th$Question_78 == 3, "Neutral",
                                          ifelse(May17th$Question_78 == 4, "Agree",
                                                 ifelse(May17th$Question_78 == 5, "Strongly Agree", NA)))))

##data_source
May17th$data_source <- ifelse(May17th$data_source == 1, "Pen and Paper survey", 
                            ifelse(May17th$data_source == 2, "Pen and Paper survey",
                                   ifelse(May17th$data_source == 3, "Qualtrics", NA)))

```

#saving clean data to cleandata folder
save_data_location = here("Primary Data Analysis ASU", "APHA","Data", "cleandata", "May17th.rds")
saveRDS(May17th, file = save_data_location)