---
title: "Elderly family member vs Risk of COVID  & Children in household vs Risk of Covid"
format: docx
editor: visual
echo: false 
---

# Library

```{r}
library(DescTools)
library(dplyr)
library(tidyr)
library(tidyverse)
library(here)
```

# Load data

```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "descriptive_summary_asu","Data", "cleandata", "Feb28.rds")
Feb28 = readRDS(data_location)

```


# table for elderly family member x "I (or my chidlren) am at risk of getting a COVID-19 infection"
```{r}
table(Feb28$Elderly_family, Feb28$Question_15)
prop.table(table(Feb28$Elderly_family, Feb28$Question_15))
chisq.test(Feb28$Elderly_family, Feb28$Question_15)
```


# table for elderly family member x " My family members are at risk of COVID-19 infection "
```{r}
table(Feb28$Elderly_family, Feb28$Question_16)
prop.table(table(Feb28$Elderly_family, Feb28$Question_16))
chisq.test(Feb28$Elderly_family, Feb28$Question_16)
```

# table for elderly family member x "  I feel knowledgeable about the risk of getting COVID-19 infection"
```{r}
table(Feb28$Elderly_family, Feb28$Question_17)
prop.table(table(Feb28$Elderly_family, Feb28$Question_17))
chisq.test(Feb28$Elderly_family, Feb28$Question_17)
```

# table for elderly family member x "I am worried about the likehood of getting a COVID-19 infection in the near future"
```{r}
table(Feb28$Elderly_family, Feb28$Question_18)
prop.table(table(Feb28$Elderly_family, Feb28$Question_18))
chisq.test(Feb28$Elderly_family, Feb28$Question_18)
```

# table for Children household x "I (or my chidlren) am at risk of getting a COVID-19 infection"
```{r}
table(Feb28$Children, Feb28$Question_15)
prop.table(table(Feb28$Children, Feb28$Question_15))
chisq.test(Feb28$Children, Feb28$Question_15)
```


# table for Children household x " My family members are at risk of COVID-19 infection "
```{r}
table(Feb28$Children, Feb28$Question_16)
prop.table(table(Feb28$Children, Feb28$Question_16))
chisq.test(Feb28$Children, Feb28$Question_16)
```

# table for Children household x "  I feel knowledgeable about the risk of getting COVID-19 infection"
```{r}
table(Feb28$Children, Feb28$Question_17)
prop.table(table(Feb28$Children, Feb28$Question_17))
chisq.test(Feb28$Children, Feb28$Question_17)
```

# table for Children household x "I am worried about the likehood of getting a COVID-19 infection in the near future"
```{r}
table(Feb28$Children, Feb28$Question_18)
prop.table(table(Feb28$Children, Feb28$Question_18))
chisq.test(Feb28$Children, Feb28$Question_18)
```

