---
title: "Descriptive Analysis of ASU Survey"
format: docx
editor: visual
echo: false
---

# Library

```{r}
library(DescTools)
library(dplyr)
library(tidyr)
library(tidyverse)
library(here)
library(pastecs)
library(naniar)
library(readxl)
library(here)
library(readxl)
library(tidyverse)
library(table1)
```

# Load data
```{r}
#importing the file with surveys up until Feb 28th 
location = here("Primary Data Analysis","APHA_Data_CutOff", "Clean_Data", "asu_merged.xlsx")

#naming the rawdata 
asu_merged = read_excel(location)
```


## Checking the varibale types
```{r}
str(asu_merged)
#converting to numeric data 
asu_merged = asu_merged %>% mutate_all(as.numeric)
str(asu_merged)
```

# Creating the Exposure variable where 1 = asu_merged and 2 = not asu_merged to COVID-19 and 3 = paricipants that left quesiton missing or answered do not know or don't know
```{r}
# Create a new variable "Exposure" with missing values by default
asu_merged$Exposure <- NA

# Set values of "Exposure" based on the values of "Question_1"
asu_merged$Exposure[asu_merged$Question_1 == 1] <- 1
asu_merged$Exposure[asu_merged$Question_1 == 2] <- 2
asu_merged$Exposure[!(asu_merged$Question_1 %in% c(1, 2))] <- 3 

table(asu_merged$Exposure)
```

#At risk Variable
```{r}
# Create a new variable "Risk" with missing values by default
asu_merged$Risk <- NA

# Set values of "Risk" based on the values of "Question_1"
asu_merged$Risk[asu_merged$Question_15 == 1] <- 1
asu_merged$Risk[asu_merged$Question_15 == 2] <- 1
asu_merged$Risk[asu_merged$Question_15 == 3] <- 2
asu_merged$Risk[asu_merged$Question_15 == 4] <- 3
asu_merged$Risk[asu_merged$Question_15 == 5] <- 3

table(asu_merged$Risk)
```

## Adding and Cleaning variables for easy-to-read descriptive analysis 
```{r}
####################################### Question Regarding the number of children that tested positive in household
asu_merged$N_Children_under5 <- NA

# Set values of "N_Children_1" based on the values of "Number_children_1"
asu_merged$N_Children_under5[asu_merged$Number_children_1 == 0] <- 0
asu_merged$N_Children_under5[asu_merged$Number_children_1 == 1] <- 1
asu_merged$N_Children_under5[asu_merged$Number_children_1 == 2] <- 2
asu_merged$N_Children_under5[!(asu_merged$Number_children_1 %in% c(1, 2, NA, "*"))] <- "3+"  

table(asu_merged$N_Children_under5)

# Create a new variable "N_Children_2" with missing values by default. This variable based on Number_children_2 asking participants the number of children that are 5-11 in household
asu_merged$N_Children_5to11 <- NA

# Set values of "N_children_2" based on the values of "Number_children_2"
asu_merged$N_Children_5to11[asu_merged$Number_children_2 == 0] <- 0
asu_merged$N_Children_5to11[asu_merged$Number_children_2 == 1] <- 1
asu_merged$N_Children_5to11[asu_merged$Number_children_2 == 2] <- 2
asu_merged$N_Children_5to11[!(asu_merged$Number_children_2 %in% c(1, 2, NA, "*"))] <- "3+" 

table(asu_merged$N_Children_5to11)

# Create a new variable "N_Children_3" with missing values by default.  This variable based on Number_children_3 asking participants the number of children that are 12-17 in household
asu_merged$N_Children_12to17 <- NA

# Set values of "N_children_2" based on the values of "Number_children_3"
asu_merged$N_Children_12to17[asu_merged$Number_children_3 == 0] <- 0
asu_merged$N_Children_12to17[asu_merged$Number_children_3 == 1] <- 1
asu_merged$N_Children_12to17[asu_merged$Number_children_3 == 2] <- 2
asu_merged$N_Children_12to17[!(asu_merged$Number_children_3 %in% c(1, 2, NA, "*"))] <- "3+"  

table(asu_merged$N_Children_12to17)

####################################### Question Regarding the number of elderly that tested positive in household
#elderly family members 65-74
asu_merged$Number_elderly_1b <- NA

# Set values of "N_children_2" based on the values of "Number_children_3"
asu_merged$Number_elderly_1b[asu_merged$Number_elderly_1 == 0] <- 0
asu_merged$Number_elderly_1b[asu_merged$Number_elderly_1 == 1] <- 1
asu_merged$Number_elderly_1b[asu_merged$Number_elderly_1 == 2] <- 2
asu_merged$Number_elderly_1b[!(asu_merged$Number_elderly_1 %in% c(0:15))] <- NA
asu_merged$Number_elderly_1b[!(asu_merged$Number_elderly_1 %in% c(1, 2, NA, "*"))] <- "3+"  

table(asu_merged$Number_elderly_1b)

#elderly family members 75+
asu_merged$Number_elderly_2b <- NA

# Set values of "N_children_2" based on the values of "Number_children_3"
asu_merged$Number_elderly_2b[asu_merged$Number_elderly_2 == 0] <- 0
asu_merged$Number_elderly_2b[asu_merged$Number_elderly_2 == 1] <- 1
asu_merged$Number_elderly_2b[asu_merged$Number_elderly_2 == 2] <- 2
asu_merged$Number_elderly_2b[!(asu_merged$Number_elderly_2 %in% c(0:15))] <- NA
asu_merged$Number_elderly_2b[!(asu_merged$Number_elderly_2 %in% c(1, 2, NA, "*"))] <- "3+"  

table(asu_merged$Number_elderly_1b)

####################################### Question 3-12 are the questions asking the age of family member with COVID-19 and How many months since infection

# Create a new variable "Question_3b" with missing values by default. 
asu_merged$Question_3b <- asu_merged$Question_3

# Set values of "Question_3" based on the values of "Number_children_3"
asu_merged$Question_3b[!(asu_merged$Question_3 %in% c(1:110))] <- NA

table(asu_merged$Question_3b)

# Create a new variable "Question_4b"
asu_merged$Question_4b <- asu_merged$Question_4 

# Set values of "Question_4b": changing years to months and anything outside 38 months will be dropped
asu_merged$Question_4b[asu_merged$Question_4 == 2020] <- 36
asu_merged$Question_4b[asu_merged$Question_4 == 2021] <- 24
asu_merged$Question_4b[asu_merged$Question_4 == 2022] <- 12
asu_merged$Question_4b[!(asu_merged$Question_4 %in% c(0:38))] <- NA

table(asu_merged$Question_4b)

# Create a new variable "Question_5b"
asu_merged$Question_5b <- asu_merged$Question_5

# Set values of "Question_5b" based on the values of "Question_5"
asu_merged$Question_5b[!(asu_merged$Question_5 %in% c(1:110))] <- NA

table(asu_merged$Question_5b)

# Create a new variable "Question_6b". 
asu_merged$Question_6b <- asu_merged$Question_6 

# Set values of "Question_6b", changing years to months and anything outside 38 months will be dropped
asu_merged$Question_6b[asu_merged$Question_6 == 2020] <- 36
asu_merged$Question_6b[asu_merged$Question_6 == 2021] <- 24
asu_merged$Question_6b[asu_merged$Question_6 == 2022] <- 12
asu_merged$Question_6b[!(asu_merged$Question_6 %in% c(0:38))] <- NA

table(asu_merged$Question_6b)

# Create a new variable "Question_7b" 
asu_merged$Question_7b <- asu_merged$Question_7

# Set values of "Question_7b" based on the values of "Question_5"
asu_merged$Question_7b[!(asu_merged$Question_7 %in% c(1:110))] <- NA

table(asu_merged$Question_7b)

# Create a new variable "Question_6b". 
asu_merged$Question_8b <- asu_merged$Question_8 

# Set values of "Question_6b", changing years to months and anything outside 38 months will be dropped
asu_merged$Question_8b[asu_merged$Question_8 == 2020] <- 36
asu_merged$Question_8b[asu_merged$Question_8 == 2021] <- 24
asu_merged$Question_8b[asu_merged$Question_8 == 2022] <- 12
asu_merged$Question_8b[!(asu_merged$Question_8 %in% c(0:38))] <- NA

table(asu_merged$Question_8b)

# Create a new variable "Question_9b" 
asu_merged$Question_9b <- asu_merged$Question_9

# Set values of "Question_9b" based on the values of "Question_9"
asu_merged$Question_9b[!(asu_merged$Question_9 %in% c(1:110))] <- NA

table(asu_merged$Question_9b)

# Create a new variable "Question_10b". 
asu_merged$Question_10b <- asu_merged$Question_10 

# Set values of "Question_10b", changing years to months and anything outside 38 months will be dropped
asu_merged$Question_10b[asu_merged$Question_10 == 2020] <- 36
asu_merged$Question_10b[asu_merged$Question_10 == 2021] <- 24
asu_merged$Question_10b[asu_merged$Question_10 == 2022] <- 12
asu_merged$Question_10b[!(asu_merged$Question_10 %in% c(0:38))] <- NA

table(asu_merged$Question_10b)

# Create a new variable "Question_11b" 
asu_merged$Question_11b <- asu_merged$Question_11

# Set values of "Question_11b" based on the values of "Question_9"
asu_merged$Question_11b[!(asu_merged$Question_11 %in% c(1:110))] <- NA

table(asu_merged$Question_11b)

# Create a new variable "Question_10b". 
asu_merged$Question_12b <- asu_merged$Question_12

# Set values of "Question_10b", changing years to months and anything outside 38 months will be dropped
asu_merged$Question_12b[asu_merged$Question_12 == 2020] <- 36
asu_merged$Question_12b[asu_merged$Question_12 == 2021] <- 24
asu_merged$Question_12b[asu_merged$Question_12 == 2022] <- 12
asu_merged$Question_12b[!(asu_merged$Question_12 %in% c(0:38))] <- NA

table(asu_merged$Question_12b)

####################################### Creating a conditions variable that has values for those with 1,2 and 3+ of the listed conditions including the category "other" 

#replacing NA values for 0
asu_merged$Conditions_Cancer[is.na(asu_merged$Conditions_Cancer)] <- 0
asu_merged$Conditions_Severe_Allergies[is.na(asu_merged$Conditions_Severe_Allergies)] <- 0
asu_merged$Conditions_Seizures[is.na(asu_merged$Conditions_Seizures)] <- 0
asu_merged$Conditions_Obesity[is.na(asu_merged$Conditions_Obesity)] <- 0
asu_merged$Conditions_Cardio_Disease[is.na(asu_merged$Conditions_Cardio_Disease)] <- 0
asu_merged$Conditions_Rheumatological[is.na(asu_merged$Conditions_Rheumatological)] <- 0
asu_merged$Conditions_Pulmonary[is.na(asu_merged$Conditions_Pulmonary)] <- 0
asu_merged$Conditions_Diabetes[is.na(asu_merged$Conditions_Diabetes)] <- 0
asu_merged$Conditions_Immuno[is.na(asu_merged$Conditions_Immuno)] <- 0
asu_merged$Conditions_Pregnancy[is.na(asu_merged$Conditions_Pregnancy)] <- 0
asu_merged$Conditions_Other[is.na(asu_merged$Conditions_Other)] <- 0
asu_merged$Conditions_No_Conditions[is.na(asu_merged$Conditions_Other)] <- 0

asu_merged$N_Conditions <- rowSums(asu_merged[, c("Conditions_Cancer", "Conditions_Severe_Allergies", "Conditions_Seizures", "Conditions_Obesity", "Conditions_Cardio_Disease", "Conditions_Rheumatological", "Conditions_Pulmonary", "Conditions_Diabetes", "Conditions_Immuno", "Conditions_Pregnancy", "Conditions_Other")])

#Seeing if it worked
table(asu_merged$N_Conditions)

#creating a more discrete variable for conditions
asu_merged$N_Conditions_b <- asu_merged$N_Conditions

asu_merged$N_Conditions_b[asu_merged$N_Conditions == 1] <- "One Conditions"
asu_merged$N_Conditions_b[asu_merged$N_Conditions == 2] <- "Two Conditions"
asu_merged$N_Conditions_b[!(asu_merged$N_Conditions %in% c(1, 2, 0, "*"))] <- "3+ Conditions"

####################################### At risk questions 
# Create a new variable "Question_16b" with missing values by default
asu_merged$Question_16b <- NA

# Set values of "Risk" based on the values of "Question_1"
asu_merged$Question_16b[asu_merged$Question_16 == 1] <- "Not At Risk"
asu_merged$Question_16b[asu_merged$Question_16 == 2] <- "Not At Risk"
asu_merged$Question_16b[asu_merged$Question_16 == 3] <- "Neutral"
asu_merged$Question_16b[asu_merged$Question_16 == 4] <- "At Risk"
asu_merged$Question_16b[asu_merged$Question_16 == 5] <- "At Risk"

table(asu_merged$Question_16b)

# Create a new variable "Question_17b" with missing values by default
asu_merged$Question_17b <- NA

# Set values of "Risk" based on the values of "Question_1"
asu_merged$Question_17b[asu_merged$Question_17 == 1] <- "Not At Risk"
asu_merged$Question_17b[asu_merged$Question_17 == 2] <- "Not At Risk"
asu_merged$Question_17b[asu_merged$Question_17 == 3] <- "Neutral"
asu_merged$Question_17b[asu_merged$Question_17 == 4] <- "At Risk"
asu_merged$Question_17b[asu_merged$Question_17 == 5] <- "At Risk"

table(asu_merged$Question_17b)

# Create a new variable "Question_18b" with missing values by default
asu_merged$Question_18b <- NA

# Set values of "Risk" based on the values of "Question_1"
asu_merged$Question_18b[asu_merged$Question_18 == 1] <- "Not At Risk"
asu_merged$Question_18b[asu_merged$Question_18 == 2] <- "Not At Risk"
asu_merged$Question_18b[asu_merged$Question_18 == 3] <- "Neutral"
asu_merged$Question_18b[asu_merged$Question_18 == 4] <- "At Risk"
asu_merged$Question_18b[asu_merged$Question_18 == 5] <- "At Risk"

table(asu_merged$Question_18b)
```
#--------------------------------------DEMOGRAPHICS---------------------------------------------------#

# Summary for zip

```{r}
asu_merged$Zip[!(asu_merged$Zip %in% c(31701, 31705, 31707))] <- "Other" 

PercTable(asu_merged$Zip)
```

# Summary for gender

```{r}
asu_merged$Exposure <- ifelse(asu_merged$Exposure == 1, "Exposed", 
                       ifelse(asu_merged$Exposure == 2, "Unexposed",
                              ifelse(asu_merged$Exposure == 3, "Missing", NA)))

asu_merged$Gender <- ifelse(asu_merged$Gender == 1, "Male", 
                       ifelse(asu_merged$Gender == 2, "Female",
                              ifelse(asu_merged$Gender == 3, "I would rather not specify", NA)))

PercTable(asu_merged$Gender)
```

# Summary for age

```{r}
##Age
asu_merged$Age <- ifelse(asu_merged$Age == 1, "18-24 years old", 
                                 ifelse(asu_merged$Age == 2, "25-34 years old",
                                        ifelse(asu_merged$Age == 3, "35-44 years old",
                                               ifelse(asu_merged$Age == 4, "45-54 years old",
                                                      ifelse(asu_merged$Age == 5, "55-64 years old",
                                                             ifelse(asu_merged$Age == 6, "65-74 years old",
                                                                    ifelse(asu_merged$Age == 7, "75 years or older", NA)))))))


PercTable(asu_merged$Age)
```

# Summary for race

```{r}
##Race_Ethnicity
asu_merged$Race_Ethnicity <- ifelse(asu_merged$Race_Ethnicity == 1, "African American", 
                                            ifelse(asu_merged$Race_Ethnicity == 2, "Caucasian",
                                                   ifelse(asu_merged$Race_Ethnicity == 3, "Latino or Hispanic",
                                                          ifelse(asu_merged$Race_Ethnicity == 4, "Asian",
                                                                 ifelse(asu_merged$Race_Ethnicity == 5, "Native American",
                                                                        ifelse(asu_merged$Race_Ethnicity == 6, "Other", NA))))))

PercTable(asu_merged$Race_Ethnicity)
```

# Summary for Education

```{r}
##Education
asu_merged$Education <- ifelse(asu_merged$Education == 1, "Less than High School", 
                          ifelse(asu_merged$Education == 2, "High School",
                                 ifelse(asu_merged$Education == 3, "Bachelor's Degree or higher", NA)))

PercTable(asu_merged$Education)
```

# Summary for Language

```{r}
##Language
asu_merged$Language <- ifelse(asu_merged$Language == 1, "English", 
                         ifelse(asu_merged$Language == 2, "Spanish",
                                ifelse(asu_merged$Language == 3, "Other", NA)))

PercTable(asu_merged$Language)
```

# Summary for Income

```{r}
##Income
asu_merged$Income <- ifelse(asu_merged$Income == 1, "Less than $25,000", 
                       ifelse(asu_merged$Income == 2, "$25,000-$50,000",
                              ifelse(asu_merged$Income == 3, "$50,000-$100,000",
                                     ifelse(asu_merged$Income == 4, "More than $100,000", NA))))

PercTable(asu_merged$Income)
```

# Summary for Family_household

```{r}
##Family_household
asu_merged$Family_household <- ifelse(asu_merged$Family_household == 1, 1, 
                                 ifelse(asu_merged$Family_household == 2, 2,
                                        ifelse(asu_merged$Family_household == 3, 3,
                                               ifelse(asu_merged$Family_household == 4, 4,
                                                      ifelse(asu_merged$Family_household == 5, "5 or more", NA)))))

PercTable(asu_merged$Family_household)
```

# Summary for Children

```{r}
##Children
asu_merged$Children <- ifelse(asu_merged$Children == 1, "Yes", 
                         ifelse(asu_merged$Children == 2, "No", NA))

PercTable(asu_merged$Children)
```

# Summary for number of children below 5 years old

```{r}
PercTable(asu_merged$N_Children_under5)
```

# Summary for number of children between 5-11

```{r}
PercTable(asu_merged$N_Children_5to11)
```

# Summary for number of children between 12-17

```{r}
PercTable(asu_merged$N_Children_12to17)
```

# Summary for elderly family members

```{r}
PercTable(asu_merged$Elderly_family)
```

# Summary for the number of elderly family members aged 65-74

```{r}
PercTable(asu_merged$Number_elderly_1b)
```

# Summary for the number of elderly family members aged 75+

```{r}
PercTable(asu_merged$Number_elderly_2b)
```

# Summary for health insurance

```{r}
##`Health Insurance`
asu_merged$`Health Insurance` <- ifelse(asu_merged$`Health Insurance` == 1, "Medicaid", 
                                                ifelse(asu_merged$`Health Insurance` == 2, "Medicare",
                                                       ifelse(asu_merged$`Health Insurance` == 3, "Affordable Care Act (Obamacare)",
                                                              ifelse(asu_merged$`Health Insurance` == 4, "Uninsured",
                                                                     ifelse(asu_merged$`Health Insurance` == 5, "Private `Health Insurance`",
                                                                            ifelse(asu_merged$`Health Insurance` == 6, "Other",
                                                                                   ifelse(asu_merged$`Health Insurance` == 7, "Don't Know / Not Sure", NA)))))))

PercTable(asu_merged$`Health Insurance`)
```

# Summary for participants with cancer

```{r}
##Conditions_Cancer
asu_merged$Conditions_Cancer <- ifelse(asu_merged$Conditions_Cancer == 1, "Yes", NA)

table(asu_merged$Conditions_Cancer)
```

# Summary for participants with severe allergies

```{r}
asu_merged$Conditions_Severe_Allergies <- ifelse(asu_merged$Conditions_Severe_Allergies == 1, "Yes", NA)

table(asu_merged$Conditions_Severe_Allergies)
```

# Summary for participants with seizures

```{r}
asu_merged$Conditions_Seizures <- ifelse(asu_merged$Conditions_Seizures == 1, "Yes", NA)

table(asu_merged$Conditions_Seizures)
```

# Summary for participants with obesity

```{r}
asu_merged$Conditions_Obesity <- ifelse(asu_merged$Conditions_Obesity == 1, "Yes", NA)

table(asu_merged$Conditions_Obesity)
```

# Summary for participants with cardiovascular disease

```{r}
asu_merged$Conditions_Cardio_Disease <- ifelse(asu_merged$Conditions_Cardio_Disease == 1, "Yes", NA)

table(asu_merged$Conditions_Cardio_Disease)
```

# Summary for participants with Rheumatological

```{r}
asu_merged$Conditions_Rheumatological <- ifelse(asu_merged$Conditions_Rheumatological == 1, "Yes", NA)

table(asu_merged$Conditions_Rheumatological)
```

# Summary for participants with pulmonary disease

```{r}
asu_merged$Conditions_Pulmonary <- ifelse(asu_merged$Conditions_Pulmonary == 1, "Yes", NA)

table(asu_merged$Conditions_Pulmonary)
```

# Summary for participants with diabetes

```{r}
asu_merged$Conditions_Diabetes <- ifelse(asu_merged$Conditions_Diabetes == 1, "Yes", NA)

table(asu_merged$Conditions_Diabetes)
```

# Summary for participants who are in an immunocompromised state

```{r}
asu_merged$Conditions_Immuno <- ifelse(asu_merged$Conditions_Immuno == 1, "Yes", NA)

table(asu_merged$Conditions_Immuno)
```

# Summary for participants who are pregnant

```{r}
asu_merged$Conditions_Pregnancy <- ifelse(asu_merged$Conditions_Pregnancy == 1, "Yes", NA)

table(asu_merged$Conditions_Pregnancy)
```

# Summary for participants who are other

```{r}
asu_merged$Conditions_Other <- ifelse(asu_merged$Conditions_Other == 1, "Yes", NA)

table(asu_merged$Conditions_Other)
```

# Summary for participants who have no health conditions

```{r}
asu_merged$Conditions_No_Conditions <- ifelse(asu_merged$Conditions_No_Conditions == 1, "Yes", NA)

table(asu_merged$Conditions_No_Conditions)
```

# Summary for participants who have conditions

```{r}
PercTable(asu_merged$N_Conditions_b)
```

# Summary for pariciapnts with no conditions

```{r}
table(asu_merged$Conditions_No_Conditions)
```

#--------------------------------------SECTION2---------------------------------------------------#

# Summary for question 1: Has a healthcare provider or a home test ever informed you or your family members that you (or your children or other family members) had COVID-19?

```{r}
##Question_1
asu_merged$Question_1 <- ifelse(asu_merged$Question_1 == 1, "Yes", 
                           ifelse(asu_merged$Question_1 == 2, "No",
                                  ifelse(asu_merged$Question_1 == 3, "Not sure",
                                         ifelse(asu_merged$Question_1 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_1)
```

# Summary for question 2: How many members of your household tested positive for COVID-19

```{r}
PercTable(asu_merged$Question_2)
```

# Summary for question 3: Age of family member 1 who had COVID-19

```{r}
table1(~ Question_3b | factor(Exposure), data = asu_merged)
```

# Summary for Question_4: How many months since family member 1 last tested positive

```{r}
table1(~ Question_4b | factor(Exposure), data = asu_merged)
```

# Summary for Question_5: Age of family member 2 who had COVID-19

```{r}
table1(~ Question_5b | factor(Exposure), data = asu_merged)
```

# Summary for Question_6: How many months since family member 2 last tested positive

```{r}
table1(~ Question_6b | factor(Exposure), data = asu_merged)
```

# Summary for Question_7: Age of family member one who 3 COVID-19

```{r}
table1(~ Question_7b | factor(Exposure), data = asu_merged)
```

#Summary for Question_8: How many months since family member 3 last tested positive

```{r}
table1(~ Question_8b | factor(Exposure), data = asu_merged)
```

#Summary for Question_9: Age of family member four who had COVID-19

```{r}
table1(~ Question_9b | factor(Exposure), data = asu_merged)
```

# Summary for Question_10: How many months since family member 4 last tested positive

```{r}
table1(~ Question_10b | factor(Exposure), data = asu_merged)
```

# Summary for Question_11: Age of family member 5 who had COVID-19

```{r}
table1(~ Question_11b | factor(Exposure), data = asu_merged)
```

# Summary for Question_12: How many months since family member 5 last tested positive

```{r}
table1(~ Question_12b | factor(Exposure), data = asu_merged)
```

# Summary for Question_13: Did your children or your family member experience Fever or chills

```{r}
table(asu_merged$Question_13_Fever, asu_merged$Exposure)
```

# Summary for Question_13_Cough: Did your children or your family member experience cough

```{r}
table(asu_merged$Question_13_Cough, asu_merged$Exposure)
```

# Summary for Question_13_Shortness_of_breath: Did your children or your family member experience Shortness_of_breath

```{r}
table(asu_merged$Question_13_Shortness_of_breath, asu_merged$Exposure)
```

# Summary for Question_13_Fatigue: Did your children or your family member experience Fatigue

```{r}
table(asu_merged$Question_13_Fatigue, asu_merged$Exposure)
```

# Summary for Question_13_Muscle_Body_Aches: Did your children or your family member experience \_Muscle_Body_Aches

```{r}
table(asu_merged$Question_13_Muscle_Body_Aches, asu_merged$Exposure)
```

# Summary for Question_13_Headache: Did your children or your family member experience Headache

```{r}
table(asu_merged$Question_13_Headache, asu_merged$Exposure)
```

# Summary for Question_13_Loss_of_Taste: Did your children or your family member experience Loss_of_Taste

```{r}
table(asu_merged$Question_13_Loss_of_Taste, asu_merged$Exposure)
```

# Summary for Question_13_Sore_Throat: Did your children or your family member experience Sore_Throat

```{r}
table(asu_merged$Question_13_Sore_Throat, asu_merged$Exposure)
```

# Summary for Question_13_Congestion: Did your children or your family member experience Congestion

```{r}
table(asu_merged$Question_13_Congestion, asu_merged$Exposure)
```

# Summary for Question_13_Nausea: Did your children or your family member experience Nausea

```{r}
table(asu_merged$Question_13_Nausea, asu_merged$Exposure)
```

# Summary for Question_13_Diarrhea: Did your children or your family member experience Diarrhea

```{r}
table(asu_merged$Question_13_Diarrhea, asu_merged$Exposure)
```

# Summary for Question_13_Asymptomatic: Did your children or your family member experience Asymptomatic

```{r}
table(asu_merged$Question_13_Asymptomatic, asu_merged$Exposure)
```

# Summary for Question_13_Other: Did your children or your family member experience other

```{r}
table(asu_merged$Question_13_Other, asu_merged$Exposure)
```

# Summary for Question_14: Describe your symptoms

```{r}
table(asu_merged$Question_14, asu_merged$Exposure)
```

# Summary for Question_15:I (or my chidlren) am at risk of getting a COVID-19

```{r}
PercTable(asu_merged$Risk)
```

# Summary for Question_16: My family members are at risk of COVID-19 infection

```{r}
PercTable(asu_merged$Question_16b)
```

# Summary for Question_17: I feel knowledgeable about the risk of getting COVID-19 infection

```{r}
PercTable(asu_merged$Question_17b)
```

# Summary for Question_18: I am worried about the likehood of getting a COVID-19 infection in the near future

```{r}
PercTable(asu_merged$Question_18b)
```

# Summary for Question_19:Can we prevent ourselves from getting infected with the COVID-19 virus and/or reduce the severity of infection if infected?

```{r}
asu_merged$Question_19 <- ifelse(asu_merged$Question_19 == 1, "Yes", 
                            ifelse(asu_merged$Question_19 == 2, "No",
                                   ifelse(asu_merged$Question_19 == 3, "Not sure",
                                          ifelse(asu_merged$Question_19 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_19)
```

# Summary for Question_20_Basic_Health: Prevention strategies - Basic health and hygiene practices (mask wearing, handwashing, etc.)

```{r}
asu_merged$Question_20_Basic_Health <- 
  ifelse(asu_merged$Question_20_Basic_Health == 1, "Yes", NA)

table(asu_merged$Question_20_Basic_Health)
```

# Summary for Question_20_COVID_19_Vacc: Prevention strategies - Staying up to date with COVID-19 vaccines

```{r}
asu_merged$Question_20_COVID_19_Vacc <- 
  ifelse(asu_merged$Question_20_COVID_19_Vacc == 1, "Yes", NA)

table(asu_merged$Question_20_COVID_19_Vacc)
```

# Summary for Question_20_Improving_ventilation: Prevention strategies

```{r}
asu_merged$Question_20_Improving_ventilation <- 
  ifelse(asu_merged$Question_20_Improving_ventilation == 1, "Yes", NA)

table(asu_merged$Question_20_Improving_ventilation)
```

# Summary for Question_20_Getting_tested: Prevention strategies

```{r}
asu_merged$Question_20_Getting_tested <- 
  ifelse(asu_merged$Question_20_Getting_tested == 1, "Yes", NA)

table(asu_merged$Question_20_Getting_tested)
```

# Summary for Question_20_Following_recommendations: Prevention strategies

```{r}
asu_merged$Question_20_Following_recommendations <- 
  ifelse(asu_merged$Question_20_Following_recommendations == 1, "Yes", NA)

table(asu_merged$Question_20_Following_recommendations)
```

# Summary for Question_20_Staying_home: Prevention strategies

```{r}
asu_merged$Question_20_Staying_home <- 
  ifelse(asu_merged$Question_20_Staying_home == 1, "Yes", NA)

table(asu_merged$Question_20_Staying_home)
```

# Summary for Question_20_Seeking: Prevention strategies - Seeking treatment if you have COVID-19 and are at a high risk of getting very sick

```{r}
asu_merged$Question_20_Seeking <- 
  ifelse(asu_merged$Question_20_Seeking == 1, "Yes", NA)

table(asu_merged$Question_20_Seeking)
```

# Summary for Question_20_Avoiding: Prevention strategies - Avoiding contact with people who have suspected or confirmed COVID-19

```{r}
asu_merged$Question_20_Avoiding <- 
  ifelse(asu_merged$Question_20_Avoiding == 1, "Yes", NA)

table(asu_merged$Question_20_Avoiding)
```

# Summary for Question_21: Do you know where to get a COVID-19 vaccine?

```{r}
asu_merged$Question_21 <- ifelse(asu_merged$Question_21 == 1, "Yes", 
                            ifelse(asu_merged$Question_21 == 2, "No",
                                   ifelse(asu_merged$Question_21 == 3, "Not sure",
                                          ifelse(asu_merged$Question_21 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_21)
```

#--------------------------------------SECTION3---------------------------------------------------#

# Summary for Question_22: Were you provided with COVID-19 health information during the event today?

```{r}
##Question_22
asu_merged$Question_22 <- ifelse(asu_merged$Question_22 == 1, "Yes", 
                            ifelse(asu_merged$Question_22 == 2, "No",
                                   ifelse(asu_merged$Question_22 == 3, "Not sure",
                                          ifelse(asu_merged$Question_22 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_22)
```

# Summary for Question_23: Did you understand the COVID-19 health information provided today?

```{r}
asu_merged$Question_23 <- ifelse(asu_merged$Question_23 == 1, "Yes", 
                            ifelse(asu_merged$Question_23 == 2, "No",
                                   ifelse(asu_merged$Question_23 == 3, "Not sure",
                                          ifelse(asu_merged$Question_23 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_23)
```

# Summary for Question_24: Did you receive information on the COVID-19 vaccine today?

```{r}
asu_merged$Question_24 <- ifelse(asu_merged$Question_24 == 1, "Yes", 
                            ifelse(asu_merged$Question_24 == 2, "No",
                                   ifelse(asu_merged$Question_24 == 3, "Not sure",
                                          ifelse(asu_merged$Question_24 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_24)
```

# Summary for Question_25: Did you also receive a COVID-19 vaccine today?

```{r}
asu_merged$Question_25 <- ifelse(asu_merged$Question_25 == 1, "Yes", 
                            ifelse(asu_merged$Question_25 == 2, "No", NA))

PercTable(asu_merged$Question_25)
```

# Summary for Question_26: Was the COVID-19 vaccine dose you received today your 1st dose?

```{r}
asu_merged$Question_26 <- ifelse(asu_merged$Question_26 == 1, "Yes", 
                            ifelse(asu_merged$Question_26 == 2, "No", NA))

PercTable(asu_merged$Question_26)
```

# Summary for Question_27: Were you vaccinated in the past?

```{r}
asu_merged$Question_27 <- ifelse(asu_merged$Question_27 == 1, "Yes", 
                            ifelse(asu_merged$Question_27 == 2, "No", NA))

PercTable(asu_merged$Question_27)
```

# Summary for Question_28: Do you plan to get vaccinated in the near future?

```{r}
asu_merged$Question_28 <- ifelse(asu_merged$Question_28 == 1, "Yes", 
                            ifelse(asu_merged$Question_28 == 2, "No",
                                   ifelse(asu_merged$Question_28 == 3, "Not sure",
                                          ifelse(asu_merged$Question_28 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_28)
```

# Summary for Question_29: If/when you decide to get vaccinated, do you know where to get a COVID-19 vaccine?

```{r}
asu_merged$Question_29 <- ifelse(asu_merged$Question_29 == 1, "Yes", 
                            ifelse(asu_merged$Question_29 == 2, "No", NA))

PercTable(asu_merged$Question_29)
```

# Summary for Question_30_Physician: Who provided the information during the event today? Physician

```{r}
asu_merged$Question_30_Physician <- 
  ifelse(asu_merged$Question_30_Physician == 1, "Yes", NA)

table(asu_merged$Question_30_Physician)
```

# Summary for Question_30_Nurse_Practitioner: Who provided the information during the event today? Nurse Practitioner

```{r}
asu_merged$Question_30_Nurse_Practitioner <- 
  ifelse(asu_merged$Question_30_Nurse_Practitioner == 1, "Yes", NA)

table(asu_merged$Question_30_Nurse_Practitioner)
```

# Summary for Question_30_Registered_Nurse: Who provided the information during the event today? Registered Nurse

```{r}
asu_merged$Question_30_Registered_Nurse <- 
  ifelse(asu_merged$Question_30_Registered_Nurse == 1, "Yes", NA)

table(asu_merged$Question_30_Registered_Nurse)
```

# Summary for Question_30_Community_Health_Advocate: Who provided the information during the event today? Community Health Advocate

```{r}
asu_merged$Question_30_Community_Health_Advocate <- 
  ifelse(asu_merged$Question_30_Community_Health_Advocate == 1, "Yes", NA)

table(asu_merged$Question_30_Community_Health_Advocate)
```

# Summary for Question_30_Community_Member: Who provided the information during the event today? Community Member

```{r}
asu_merged$Question_30_Community_Member <- 
  ifelse(asu_merged$Question_30_Community_Member == 1, "Yes", NA)

table(asu_merged$Question_30_Community_Member)
```

# Summary for Question_30_Other: Who provided the information during the event today? Other

```{r}
asu_merged$Question_30_Other <- 
  ifelse(asu_merged$Question_30_Other == 1, "Yes", NA)

table(asu_merged$Question_30_Other)
```

# Summary for Question_31: Who provided the information during the event today? specify

```{r}
table(asu_merged$Question_31)
```

# Summary for Question_32: Did the information provider during the event today check your understanding of the COVID-19 health information provided including information about the vaccine?

```{r}
asu_merged$Question_32 <- ifelse(asu_merged$Question_32 == 1, "Yes", 
                            ifelse(asu_merged$Question_32 == 2, "No",
                                   ifelse(asu_merged$Question_32 == 3, "Not sure",
                                          ifelse(asu_merged$Question_32 == 4, "Do not know", NA))))

table(asu_merged$Question_32)
```

# Summary for Question_33: Were you satisfied with the communication regarding COVID-19 health information including information about the vaccine during the event today?

```{r}
asu_merged$Question_33 <- ifelse(asu_merged$Question_33 == 1, "Yes", 
                            ifelse(asu_merged$Question_33 == 2, "No",
                                   ifelse(asu_merged$Question_33 == 3, "Not sure",
                                          ifelse(asu_merged$Question_33 == 4, "Do not know", NA))))

table(asu_merged$Question_33)
```

# Summary for Question_34: Were you involved in decisions regarding COVID-19 vaccination decisions made today?

```{r}
asu_merged$Question_34 <- ifelse(asu_merged$Question_34 == 1, "Yes", 
                            ifelse(asu_merged$Question_34 == 2, "No",
                                   ifelse(asu_merged$Question_34 == 3, "Not sure",
                                          ifelse(asu_merged$Question_34 == 4, "Do not know", NA))))

table(asu_merged$Question_34)
```

# Summary for Question_35: How confident are you about COVID 19 vaccine after participating in the event today?

```{r}
asu_merged$Question_35 <- ifelse(asu_merged$Question_35 == 1, "Very confident", 
                            ifelse(asu_merged$Question_35 == 2, "Moderately confident",
                                   ifelse(asu_merged$Question_35 == 3, "Moderately unconfident",
                                          ifelse(asu_merged$Question_35 == 4, "Very unconfident", NA))))


PercTable(asu_merged$Question_35)
```

# Summary for Question_36: Was the information session you participated in today hosted by a

```{r}
asu_merged$Question_36 <- ifelse(asu_merged$Question_36 == 1, "local church", 
                                         ifelse(asu_merged$Question_36 == 2, "local hospital",
                                                ifelse(asu_merged$Question_36 == 3, "local barbershop",
                                                       ifelse(asu_merged$Question_36 == 4, "mobile vaccine and/or testing clinics",
                                                              ifelse(asu_merged$Question_36 == 5,  "other community event", NA)))))

PercTable(asu_merged$Question_36)
```

# Summary for Question_37: Please provide the name of the person (s) or organization (s) who provided the information

```{r}
PercTable(asu_merged$Question_37)
```

# Summary for Question_38_Handout_flier: How did you hear about the activity you attended today? Handout flier, pamphlet, or brochure

```{r}
asu_merged$Question_38_Handout_flier <- 
  ifelse(asu_merged$Question_38_Handout_flier == 1, "Yes", NA)

table(asu_merged$Question_38_Handout_flier)
```

# Summary for Question_38_Social_media: How did you hear about the activity you attended today? Social media (TikTok, Instagram, Facebook and Twitter)

```{r}
asu_merged$Question_38_Social_media <- 
  ifelse(asu_merged$Question_38_Social_media == 1, "Yes", NA)

table(asu_merged$Question_38_Social_media)
```

# Summary for Question_38_Standard_media: How did you hear about the activity you attended today? standard medial source (TV, Radio, Newspaper)

```{r}
asu_merged$Question_38_Standard_media <- 
  ifelse(asu_merged$Question_38_Standard_media == 1, "Yes", NA)

table(asu_merged$Question_38_Standard_media)
```

# Summary for Question_38_Community_Health_Advocate: How did you hear about the activity you attended today? A community health advocate or any other community professional

```{r}
asu_merged$Question_38_Community_Health_Advocate <- 
  ifelse(asu_merged$Question_38_Community_Health_Advocate == 1, "Yes", NA)

table(asu_merged$Question_38_Community_Health_Advocate)
```

# Summary for Question_38_Church_service: How did you hear about the activity you attended today? church service

```{r}
asu_merged$Question_38_Church_service <- 
  ifelse(asu_merged$Question_38_Church_service == 1, "Yes", NA)

table(asu_merged$Question_38_Church_service)
```

# Summary for Question_38_Barbershop: How did you hear about the activity you attended today? at the local barbershop

```{r}
asu_merged$Question_38_Barbershop <- 
  ifelse(asu_merged$Question_38_Barbershop == 1, "Yes", NA)

table(asu_merged$Question_38_Barbershop)
```

# Summary for Question_38_Community_members: How did you hear about the activity you attended today? from community members, friends, or family members

```{r}
asu_merged$Question_38_Community_members <- 
  ifelse(asu_merged$Question_38_Community_members == 1, "Yes", NA)

table(asu_merged$Question_38_Community_members)
```

# Summary for Question_38_Others: How did you hear about the activity you attended today? other

```{r}
asu_merged$Question_38_Others <- 
  ifelse(asu_merged$Question_38_Others == 1, "Yes", NA)

table(asu_merged$Question_38_Others)
```

# Summary for Question_39: How did you hear about the activity you attended today? specify

```{r}
table(asu_merged$Question_39)
```

# Summary for Question_40: Did your child or children also receive a COVID-19 vaccine today?

```{r}
asu_merged$Question_40 <- ifelse(asu_merged$Question_40 == 1, "Yes", 
                            ifelse(asu_merged$Question_40 == 2, "No",
                                   ifelse(asu_merged$Question_40 == 3, "I do not have childen under 18 in my household", NA)))

PercTable(asu_merged$Question_40)
```

# Summary for Question_41: was the dose you child/children received today their 1st dose

```{r}
asu_merged$Question_41 <- ifelse(asu_merged$Question_41 == 1, "Yes", 
                            ifelse(asu_merged$Question_41 == 2, "No", NA))

PercTable(asu_merged$Question_41)
```

# Summary for Question_42: was your child/children vaccinated in the past?

```{r}
asu_merged$Question_42 <- ifelse(asu_merged$Question_42 == 1, "Yes", 
                            ifelse(asu_merged$Question_42 == 2, "No", NA))

PercTable(asu_merged$Question_42)
```

# Summary for Question_43: do you plan to get you child/children vaccinated in the near future?

```{r}
asu_merged$Question_43 <- ifelse(asu_merged$Question_43 == 1, "Yes", 
                                         ifelse(asu_merged$Question_43 == 2, "No",
                                                ifelse(asu_merged$Question_43 == 3, "Not sure",
                                                       ifelse(asu_merged$Question_43 == 4, "Do not know", NA))))

PercTable(asu_merged$Question_43)
```

#--------------------------------------SECTION4---------------------------------------------------# Vaccine Hesitancy Qustions

# Clinical Barriers

## Summary for Question_44: Getting sick from multiple dose of COVID-19 vaccine is of concern

```{r}
asu_merged$Question_44 <- ifelse(asu_merged$Question_44 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_44 == 2, "Disagree",
                                   ifelse(asu_merged$Question_44 == 3, "Neutral",
                                          ifelse(asu_merged$Question_44 == 4, "Agree",
                                                 ifelse(asu_merged$Question_44 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_44)
```

# Summary for Question_45: Dying from the COVID-19 vaccine is of concern

```{r}
asu_merged$Question_45 <- ifelse(asu_merged$Question_45 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_45 == 2, "Disagree",
                                   ifelse(asu_merged$Question_45 == 3, "Neutral",
                                          ifelse(asu_merged$Question_45 == 4, "Agree",
                                                 ifelse(asu_merged$Question_45 == 5, "Strongly Agree", NA)))))


PercTable(asu_merged$Question_45)
```

# Summary for Question_46: Heart disease from the COVID-19 vaccine is of concern

```{r}
asu_merged$Question_46 <- ifelse(asu_merged$Question_46 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_46 == 2, "Disagree",
                                   ifelse(asu_merged$Question_46 == 3, "Neutral",
                                          ifelse(asu_merged$Question_46 == 4, "Agree",
                                                 ifelse(asu_merged$Question_46 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_46)
```

# Summary for Question_47: Blood clots from the COVID-19 vaccine is of concern

```{r}
asu_merged$Question_47 <- ifelse(asu_merged$Question_47 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_47 == 2, "Disagree",
                                   ifelse(asu_merged$Question_47 == 3, "Neutral",
                                          ifelse(asu_merged$Question_47 == 4, "Agree",
                                                 ifelse(asu_merged$Question_47 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_47)
```

# Summary for Question_48: The COVID-19 vaccine leads to miscarriages and is not appropriate for pregnant women

```{r}
asu_merged$Question_48 <- ifelse(asu_merged$Question_48 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_48 == 2, "Disagree",
                                   ifelse(asu_merged$Question_48 == 3, "Neutral",
                                          ifelse(asu_merged$Question_48 == 4, "Agree",
                                                 ifelse(asu_merged$Question_48 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_48)
```

# Summary for Question_49: High blood pressure from the COVID-19 vaccine is of concern

```{r}
asu_merged$Question_49 <- ifelse(asu_merged$Question_49 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_49 == 2, "Disagree",
                                   ifelse(asu_merged$Question_49 == 3, "Neutral",
                                          ifelse(asu_merged$Question_49 == 4, "Agree",
                                                 ifelse(asu_merged$Question_49 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_49)
```

# Summary for Question_50: COVID-19 vaccine implants a "computer chip" in the body

```{r}
asu_merged$Question_50 <- ifelse(asu_merged$Question_50 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_50 == 2, "Disagree",
                                   ifelse(asu_merged$Question_50 == 3, "Neutral",
                                          ifelse(asu_merged$Question_50 == 4, "Agree",
                                                 ifelse(asu_merged$Question_50 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_50)
```

# Summary for Question_51: COVID-19 vaccine components remain in the human body for a long period of time

```{r}
asu_merged$Question_51 <- ifelse(asu_merged$Question_51 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_51 == 2, "Disagree",
                                   ifelse(asu_merged$Question_51 == 3, "Neutral",
                                          ifelse(asu_merged$Question_51 == 4, "Agree",
                                                 ifelse(asu_merged$Question_51 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_51)
```

# Summary for Question_52: Pain from/related to COVID-19 vaccine is of concern.

```{r}
asu_merged$Question_52 <- ifelse(asu_merged$Question_52 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_52 == 2, "Disagree",
                                   ifelse(asu_merged$Question_52 == 3, "Neutral",
                                          ifelse(asu_merged$Question_52 == 4, "Agree",
                                                 ifelse(asu_merged$Question_52 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_52)
```

# Summary for Question_53: COVID-19 vaccine is NOT an effective way to protect against COVID-19.

```{r}
asu_merged$Question_53 <- ifelse(asu_merged$Question_53 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_53 == 2, "Disagree",
                                   ifelse(asu_merged$Question_53 == 3, "Neutral",
                                          ifelse(asu_merged$Question_53 == 4, "Agree",
                                                 ifelse(asu_merged$Question_53 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_53)
```

# Access Barriers

# Summary for Question_54: I don't know how to get a hold of the COVID-19 vaccine

```{r}
asu_merged$Question_54 <- ifelse(asu_merged$Question_54 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_54 == 2, "Disagree",
                                   ifelse(asu_merged$Question_54 == 3, "Neutral",
                                          ifelse(asu_merged$Question_54 == 4, "Agree",
                                                 ifelse(asu_merged$Question_54 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_54)
```

# Summary for Question_55: : It is inconvenient to get the COVID-19 vaccine

```{r}
asu_merged$Question_55 <- ifelse(asu_merged$Question_55 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_55 == 2, "Disagree",
                                   ifelse(asu_merged$Question_55 == 3, "Neutral",
                                          ifelse(asu_merged$Question_55 == 4, "Agree",
                                                 ifelse(asu_merged$Question_55 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_55)
```

# Summary for Question_56: : There is a shortage of the COVID-19 vaccine

```{r}
asu_merged$Question_56 <- ifelse(asu_merged$Question_56 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_56 == 2, "Disagree",
                                   ifelse(asu_merged$Question_56 == 3, "Neutral",
                                          ifelse(asu_merged$Question_56 == 4, "Agree",
                                                 ifelse(asu_merged$Question_56 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_56)
```

# Summary for Question_57: : The clinics/venues that provide the COVID-19 vaccine are too far away

```{r}
asu_merged$Question_57 <- ifelse(asu_merged$Question_57 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_57 == 2, "Disagree",
                                   ifelse(asu_merged$Question_57 == 3, "Neutral",
                                          ifelse(asu_merged$Question_57 == 4, "Agree",
                                                 ifelse(asu_merged$Question_57 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_57)
```

# Information Barriers

# Summary for Question_58: : I don't have enough information to decide whether to take COVID-19 vaccine or no

```{r}
asu_merged$Question_58 <- ifelse(asu_merged$Question_58 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_58 == 2, "Disagree",
                                   ifelse(asu_merged$Question_58 == 3, "Neutral",
                                          ifelse(asu_merged$Question_58 == 4, "Agree",
                                                 ifelse(asu_merged$Question_58 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_58)
```

# Summary for Question_59: : I am confused by the information about the COVID-19 vaccines

```{r}
asu_merged$Question_59 <- ifelse(asu_merged$Question_59 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_59 == 2, "Disagree",
                                   ifelse(asu_merged$Question_59 == 3, "Neutral",
                                          ifelse(asu_merged$Question_59 == 4, "Agree",
                                                 ifelse(asu_merged$Question_59 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_59)
```

# Summary for Question_60: : I don't know where I can get accurate information about the COVID-19 vaccines

```{r}
asu_merged$Question_60 <- ifelse(asu_merged$Question_60 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_60 == 2, "Disagree",
                                   ifelse(asu_merged$Question_60 == 3, "Neutral",
                                          ifelse(asu_merged$Question_60 == 4, "Agree",
                                                 ifelse(asu_merged$Question_60 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_60)
```

# Summary for Question_61: : I don't know where I can get trustworthy information about the COVID-19 vaccines

```{r}
asu_merged$Question_61 <- ifelse(asu_merged$Question_61 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_61 == 2, "Disagree",
                                   ifelse(asu_merged$Question_61 == 3, "Neutral",
                                          ifelse(asu_merged$Question_61 == 4, "Agree",
                                                 ifelse(asu_merged$Question_61 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_61)
```

# Trust Barriers

# Summary for Question_62: : I don't trust vaccines in general

```{r}
asu_merged$Question_62 <- ifelse(asu_merged$Question_62 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_62 == 2, "Disagree",
                                   ifelse(asu_merged$Question_62 == 3, "Neutral",
                                          ifelse(asu_merged$Question_62 == 4, "Agree",
                                                 ifelse(asu_merged$Question_62 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_62)
```

# Summary for Question_63: : I don't trust the scientists/professionals who recommend the COVID-19 vaccines

```{r}
asu_merged$Question_63 <- ifelse(asu_merged$Question_63 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_63 == 2, "Disagree",
                                   ifelse(asu_merged$Question_63 == 3, "Neutral",
                                          ifelse(asu_merged$Question_63 == 4, "Agree",
                                                 ifelse(asu_merged$Question_63 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_63)
```

# Summary for Question_64: : I don't trust the government agencies that approved the COVID-19 vaccines

```{r}
asu_merged$Question_64 <- ifelse(asu_merged$Question_64 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_64 == 2, "Disagree",
                                   ifelse(asu_merged$Question_64 == 3, "Neutral",
                                          ifelse(asu_merged$Question_64 == 4, "Agree",
                                                 ifelse(asu_merged$Question_64 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_64)
```

# Summary for Question_65: : I don't trust the pharmaceutical companies that manufacture the COVID-19 vaccines

```{r}
asu_merged$Question_65 <- ifelse(asu_merged$Question_65 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_65 == 2, "Disagree",
                                   ifelse(asu_merged$Question_65 == 3, "Neutral",
                                          ifelse(asu_merged$Question_65 == 4, "Agree",
                                                 ifelse(asu_merged$Question_65 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_65)
```

# Summary for Question_66: : I don't trust media that recommend the COVID-19 vaccines

```{r}
asu_merged$Question_66 <- ifelse(asu_merged$Question_66 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_66 == 2, "Disagree",
                                   ifelse(asu_merged$Question_66 == 3, "Neutral",
                                          ifelse(asu_merged$Question_66 == 4, "Agree",
                                                 ifelse(asu_merged$Question_66 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_66)
```

# Religious Barriers

# Summary for Question_67: : As long as I am faithful to my God and/or my religion, I am protected from COVID-19, therefore I do not need the COVID-19 vaccine

```{r}
asu_merged$Question_67 <- ifelse(asu_merged$Question_67 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_67 == 2, "Disagree",
                                   ifelse(asu_merged$Question_67 == 3, "Neutral",
                                          ifelse(asu_merged$Question_67 == 4, "Agree",
                                                 ifelse(asu_merged$Question_67 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_67)
```

# Summary for Question_68: : The COVID-19 vaccines' ingredients are banned by my religion therefore I cannot get the COVID-19 vaccine

```{r}
asu_merged$Question_68 <- ifelse(asu_merged$Question_68 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_68 == 2, "Disagree",
                                   ifelse(asu_merged$Question_68 == 3, "Neutral",
                                          ifelse(asu_merged$Question_68 == 4, "Agree",
                                                 ifelse(asu_merged$Question_68 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_68)
```

# Summary for Question_69: : It is better to use spiritual/holy preventive measures (e.g., holy water, holy oil, cross, holy amulets, etc.) to prevent getting sick from COVID-19 than

```{r}
asu_merged$Question_69 <- ifelse(asu_merged$Question_69 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_69 == 2, "Disagree",
                                   ifelse(asu_merged$Question_69 == 3, "Neutral",
                                          ifelse(asu_merged$Question_69 == 4, "Agree",
                                                 ifelse(asu_merged$Question_69 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_69)
```

# Summary for Question_70: : It is better to use natural preventive methods (e.g., essential oils, other natural drinks, tonics etc.) to prevent getting infected with COVID-19 than getting the vaccine

```{r}
asu_merged$Question_70 <- ifelse(asu_merged$Question_70 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_70 == 2, "Disagree",
                                   ifelse(asu_merged$Question_70 == 3, "Neutral",
                                          ifelse(asu_merged$Question_70 == 4, "Agree",
                                                 ifelse(asu_merged$Question_70 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_70)
```

# Summary for Question_71: : It is better to get sick of COVID-19 and for your body to fight it off, building natural immunity than getting the vaccine rinks, tonics etc.) to prevent getting infected with COVID-19 than getting the vaccine

```{r}
asu_merged$Question_71 <- ifelse(asu_merged$Question_71 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_71 == 2, "Disagree",
                                   ifelse(asu_merged$Question_71 == 3, "Neutral",
                                          ifelse(asu_merged$Question_71 == 4, "Agree",
                                                 ifelse(asu_merged$Question_71 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_71)
```

#--------------------------------------SECTION5---------------------------------------------------#

# Summary for Question_72: : I am willing to get vaccinated if The CDC/ local health department recommended us to get the COVID-19 vaccine

```{r}
asu_merged$Question_72 <- ifelse(asu_merged$Question_72 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_72 == 2, "Disagree",
                                   ifelse(asu_merged$Question_72 == 3, "Neutral",
                                          ifelse(asu_merged$Question_72 == 4, "Agree",
                                                 ifelse(asu_merged$Question_72 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_72)
```

# Summary for Question_73: : I am willing to get vaccinated if My health care provider recommended me to get the COVID-19 vaccine

```{r}
asu_merged$Question_73 <- ifelse(asu_merged$Question_73 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_73 == 2, "Disagree",
                                   ifelse(asu_merged$Question_73 == 3, "Neutral",
                                          ifelse(asu_merged$Question_73 == 4, "Agree",
                                                 ifelse(asu_merged$Question_73 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_73)
```

# Summary for Question_74: : I am willing to get vaccinated if My nurse recommended me to get the COVID-19 vaccine

```{r}
asu_merged$Question_74 <- ifelse(asu_merged$Question_74 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_74 == 2, "Disagree",
                                   ifelse(asu_merged$Question_74 == 3, "Neutral",
                                          ifelse(asu_merged$Question_74 == 4, "Agree",
                                                 ifelse(asu_merged$Question_74 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_74)
```

# Summary for Question_75: : I am willing to get vaccinated if My spiritual advisor (such as pastor/priest/rabbi/imam) recommended me to get the COVID-19 vaccine

```{r}
asu_merged$Question_75 <- ifelse(asu_merged$Question_75 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_75 == 2, "Disagree",
                                   ifelse(asu_merged$Question_75 == 3, "Neutral",
                                          ifelse(asu_merged$Question_75 == 4, "Agree",
                                                 ifelse(asu_merged$Question_75 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_75)
```

# Summary for Question_76: : I am willing to get vaccinated if My family members recommended me to get the COVID-19 vaccine

```{r}
asu_merged$Question_76 <- ifelse(asu_merged$Question_76 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_76 == 2, "Disagree",
                                   ifelse(asu_merged$Question_76 == 3, "Neutral",
                                          ifelse(asu_merged$Question_76 == 4, "Agree",
                                                 ifelse(asu_merged$Question_76 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_76)
```

# Summary for Question_77: : I am willing to get vaccinated if My colleagues/co-workers recommended me to get the COVID-19 vaccine

```{r}
asu_merged$Question_77 <- ifelse(asu_merged$Question_77 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_77 == 2, "Disagree",
                                   ifelse(asu_merged$Question_77 == 3, "Neutral",
                                          ifelse(asu_merged$Question_77 == 4, "Agree",
                                                 ifelse(asu_merged$Question_77 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_77)
```

# Summary for Question_78: : I am willing to get vaccinated if...- I need to learn more about COVID-19 vaccination, its side effects, benefits, and future implications

```{r}
asu_merged$Question_78 <- ifelse(asu_merged$Question_78 == 1, "Strongly Disagree", 
                            ifelse(asu_merged$Question_78 == 2, "Disagree",
                                   ifelse(asu_merged$Question_78 == 3, "Neutral",
                                          ifelse(asu_merged$Question_78 == 4, "Agree",
                                                 ifelse(asu_merged$Question_78 == 5, "Strongly Agree", NA)))))

PercTable(asu_merged$Question_78)
```

# Summary for data_source: pen and paper or qualtrics

```{r}
##data_source
asu_merged$data_source <- ifelse(asu_merged$data_source == 1, "Pen and Paper survey", 
                            ifelse(asu_merged$data_source == 2, "Pen and Paper survey",
                                   ifelse(asu_merged$data_source == 3, "Qualtrics", NA)))

PercTable(asu_merged$data_source)
```
