---
title: "2x2 Tables for Question 1"
format: docx
editor: visual
echo: false 
---

# Library

```{r}
library(DescTools)
library(dplyr)
library(tidyr)
library(tidyverse)
library(here)
```

# Load data

```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "descriptive_summary_asu","Data", "cleandata", "Feb28.rds")
Feb28 = readRDS(data_location)

```

# table for Question 1 x Zip code
```{r}
table(Feb28$Question_1, Feb28$Zip)
prop.table(table(Feb28$Question_1, Feb28$Zip))
chisq.test(Feb28$Question_1, Feb28$Zip)
```

# table for Question 1 x Gender
```{r}
table(Feb28$Question_1, Feb28$Gender)
prop.table(table(Feb28$Question_1, Feb28$Gender))
chisq.test(Feb28$Question_1, Feb28$Gender)
```

# table for Question 1 x  Age
```{r}
table(Feb28$Question_1, Feb28$Age)
prop.table(table(Feb28$Question_1, Feb28$Age))
chisq.test(Feb28$Question_1, Feb28$Age)
```

# table for Question 1 x Race
```{r}
table(Feb28$Question_1, Feb28$Race_Ethnicity)
prop.table(table(Feb28$Question_1, Feb28$Race_Ethnicity))
chisq.test(Feb28$Question_1, Feb28$Race_Ethnicity)
```

# table for Question 1 x Education
```{r}
table(Feb28$Question_1, Feb28$Education)
prop.table(table(Feb28$Question_1, Feb28$Education))
chisq.test(Feb28$Question_1, Feb28$Education)
```

# table for Question 1 x  Income
```{r}
table(Feb28$Question_1, Feb28$Income)
prop.table(table(Feb28$Question_1, Feb28$Income))
chisq.test(Feb28$Question_1, Feb28$Income)
```

# table for Question 1 x "do you have elderly family memebers in your household?"
```{r}
table(Feb28$Question_1, Feb28$Elderly_family)
prop.table(table(Feb28$Question_1, Feb28$Elderly_family))
chisq.test(Feb28$Question_1, Feb28$Elderly_family)
```


# table for Question 1 x Question 2 "How many members of your household tested positive for COVID-19"

```{r}
table(Feb28$Question_1, Feb28$Question_2)
prop.table(table(Feb28$Question_1, Feb28$Question_2))
```

# table for Question 1 x Question_44: "Getting sick from multiple dose of COVID-19 vaccine is of concern"
```{r}
table(Feb28$Question_1, Feb28$Question_44)
prop.table(table(Feb28$Question_1, Feb28$Question_44))
```


