---
title: "Description of symptoms"
format: docx
editor: visual
echo: false 
---

# Library

```{r}
library(DescTools)
library(dplyr)
library(tidyr)
library(tidyverse)
library(here)
```

# Load data

```{r}
## Loading 
data_location = here("Primary Data Analysis ASU", "descriptive_summary_asu","Data", "cleandata", "Feb28.rds")
Feb28 = readRDS(data_location)

```

# table for just symptoms

```{r}
table(Feb28$Question_13_Asymptomatic)
prop.table(table(Feb28$Question_13_Asymptomatic))
```

# table Question_13_Asymptomatic

```{r}
Asympotomatic = Feb28$Question_13_Asymptomatic %>% replace(is.na(.), "*")
table(Asympotomatic)
prop.table(table(Asympotomatic))
```

# table Question_13_Fever

```{r}
Fever = Feb28$Question_13_Fever %>% replace(is.na(.), "*")
table(Fever)
prop.table(table(Fever))
```

# table Question_13_Cough

```{r}
Cough = Feb28$Question_13_Cough %>% replace(is.na(.), "*")
table(Cough)
prop.table(table(Cough))
```

# table Question_13_Shortness_of_breath

```{r}
Shortness_of_breath = Feb28$Question_13_Shortness_of_breath %>% replace(is.na(.), "*")
table(Shortness_of_breath)
prop.table(table(Shortness_of_breath))
```

# table Question_13_Fatigue

```{r}
Fatigue = Feb28$Question_13_Fatigue %>% replace(is.na(.), "*")
table(Fatigue)
prop.table(table(Fatigue))
```

# table Question_13_Muscle_Body_Aches

```{r}
Muscle_Body_Aches = Feb28$Question_13_Muscle_Body_Aches %>% replace(is.na(.), "*")
table(Muscle_Body_Aches)
prop.table(table(Muscle_Body_Aches))
```

# table Question_13_Headache

```{r}
Headache = Feb28$Question_13_Headache %>% replace(is.na(.), "*")
table(Headache)
prop.table(table(Headache))
```

# table Question_13_Loss_of_Taste

```{r}
Loss_of_Taste = Feb28$Question_13_Loss_of_Taste %>% replace(is.na(.), "*")
table(Loss_of_Taste)
prop.table(table(Loss_of_Taste))
```

# table Question_13_Sore_Throat

```{r}
Sore_Throat = Feb28$Question_13_Sore_Throat %>% replace(is.na(.), "*")
table(Sore_Throat)
prop.table(table(Sore_Throat))
```

# table Question_13_Congestion

```{r}
Congestion = Feb28$Question_13_Congestion %>% replace(is.na(.), "*")
table(Congestion)
prop.table(table(Congestion))
```

# table Question_13_Nausea

```{r}
Nausea = Feb28$Question_13_Nausea %>% replace(is.na(.), "*")
table(Nausea)
prop.table(table(Nausea))
```

# table Question_13_Diarrhea

```{r}
Diarrhea = Feb28$Question_13_Diarrhea %>% replace(is.na(.), "*")
table(Diarrhea)
prop.table(table(Diarrhea))
```

# table Question_13_Other

```{r}
Other = Feb28$Question_13_Other %>% replace(is.na(.), "*")
table(Other)
prop.table(table(Other))
```
